---
title: "Gleaner Universe"
output:
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 72
    toc: yes
---


### Explore data:  
How many bats do I have for each species?  
How many bats did I have in total?  
How many exemplars did I have for each playback?  
When were they used? (haven't done yet, should add)  

------------------------------------------------------------------------

### Questions:

#### Non-statistical:   

**Which and how many bat species approach or attack potential prey sounds?**   
      -(which are possible eavesdropping gleaners)  
      - 'Attacks' are our clearest data- if a bat landed on the speaker playing the sound, we have high confidence they are gleaners  
      - 'Approaches' are suggestive, but could also happen for other reasons (just passing close to speaker).             - So these cases are of high interest but with caution  

***Which* potential prey sounds does each bat species approach?**  
(what do they eat, if they do?)  

**Does each bat species approach mating calls, incidental sounds, or both?**  
(what kind of sounds do they use)  

**How many categories of calls does each species approach?**  
(are they specialists? generalists?)  


#### Statistical:   

**Which sounds are more attractive to more bats?**  
      Does each bat species have a similar level of response to the different prey sounds?:   
      1. are bat species similar to one another in their preferences? 
      2. are some prey consistently more attractive, or do different bat species differ?

      **Approach:**  
      Cumulative link mixed model:
      Response variable: Bat interest score  
      Fixed effects: bat species, sound type  
      Random effects: bat ID (means I will have to have enough individuals per species)  
      Bat interest score \~ bat species \* sound type (random=batID), family = logit AICc to rank models (Committee suggested iterative model selection)   
      Main effect of call type = prey categories face different levels of bat predation  
      Main effect of bat species = different bats have different levels of responsiveness to sounds  
      *Interaction between 'bat species' and 'call type' = different bats are attracted to different calls*  
      *Do some bat species approach more categories of sounds than others? (generalists v specialists)*   
        
      Kruskal--Wallis OR generalized linear mixed model (depending on data distribution)  
      Y = \# categories approached  
      x = bat species  
      Random = bat ID  
      #categories approached \~ bat species, random= bat ID, family=poisson  

---

**Which sound parameters are relevant to the preferences of each bat species?**  
(what does each bat pay attention to?)  
Cumulative link mixed models:  
      Response variable: Bat species interest score  
      Fixed effects: \#pulses\*, peak frequency, duty cycle, bandwidth, and duration  
      Random effects: bat ID AICc to rank models (ACTUALLY- iterative model selection/ e.g. maximum liklihood (module 17))  
      When highest-ranking models are nested: test for significant differences with likelihood ratio test  
      When no significant differences between models, select most parsimonious model with only significant variables  
      Which variables are included in the final model?

*May be hard to compare incidental noises with calls*  

**How do the categories of sounds cluster in acoustic space?**
PCA

**How do bat species preferences cluster?**  


**OVERALL, what matters for bat response?**  
(giant model with all variables?) response \~ bat species, prey species, prey category, amplitude, (other call characteristics), bat traits?? (mean size, wing area, etc)  

would be good to seperate out bats that, more like AJs, are just listening to sounds in their environment, vs bats taht might be using the sounds to hunt

### TO DO

Acoustic data:  
The acoustic data in the file are currently just the average value for each playback type, rather than the value for the exact call used in a trial. I need to delete these values, and match the values used in another file (call analysis) to each set and playback  
 
 Also, plot call duration and other acoustic values to find out how well automatic classification did 

Analysis/ visualization
Think about comparing all bats to the responses of AJs, to compare what it looks like when a bat is just listening to sounds as things in their environment, vs using them to hunt

------------------------------------------------------------------------


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load libraries
```{r libraries}
#library(GmAMisc) 
library(tidyverse)
library(readxl)
library(ggplot2)
#library(dplyr)
library(ggthemes)
library(RColorBrewer)
library(plotly)
library(car)
library(ordinal) 
library(emmeans)
library(multcompView)
library(broom.mixed) 
library(forcats)
library(plotly)
library(boot)
library(egg)
```
Bootstrapping functions
```{r functions}
# functions for bootstrapping 95% confidence intervals around the mean

# get mean and 95% CI of values x via bootstrapping
boot_ci <- function(x, perms=5000, bca=F) {
  get_mean <- function(x, d) {
    return(mean(x[d]))
  } 
  x <- as.vector(na.omit(x))
  mean <- mean(x)
  if(bca){
    boot <- boot.ci(boot(data=x, 
                         statistic=get_mean, 
                         R=perms, 
                         parallel = "multicore", 
                         ncpus = 4), 
                    type="bca")
    low <- boot$bca[1,4]
    high <- boot$bca[1,5] 
  }else{
    boot <- boot.ci(boot(data=x, 
                         statistic=get_mean, 
                         R=perms, 
                         parallel = "multicore", 
                         ncpus = 4), 
                    type="perc")
    low <- boot$perc[1,4]
    high <- boot$perc[1,5] 
  }
  c(low=low,mean=mean,high=high, N=round(length(x)))
}


# get mean and 95% CI via bootstrapping of values y within grouping variable x
boot_ci2 <- function(d=d, y=d$y, x=d$x, perms=5000, bca=F){
  df <- data.frame(effect=unique(x))
  df$low <- NA
  df$mean <- NA
  df$high <- NA
  df$n.obs <- NA
  for (i in 1:nrow(df)) {
    ys <- y[which(x==df$effect[i])] #pulls out all the e.g.location prefs
    if (length(ys)>1 & var(ys)>0 ){
      b <- boot_ci(y[which(x==df$effect[i])], perms=perms, bca=bca) #resamples with replacement the mean and ci for e.g. AJs pref for location, gives back the low mean and high
      df$low[i] <- b[1]
      df$mean[i] <- b[2]
      df$high[i] <- b[3]
      df$n.obs[i] <- b[4]
    }else{
      df$low[i] <- min(ys)
      df$mean[i] <- mean(ys)
      df$high[i] <- max(ys)
      df$n.obs[i] <- length(ys)
    }
  }
  df
}
# y = response score, x= response within group (e.g. bat spp)
```


### Function for ranking models (Code originally modified from supplemental R code in Bolker et al. (2009).
```{r}
# Code originally modified from supplemental R code in Bolker et al. (2009)

rankModels = function(mod,names=NULL,phi=NULL,pretend=NULL) {
  
  # Overdispersion
  # calculate Pearson Chi squared
  if (is.null(phi)==FALSE) {
    if (is.numeric(phi)){phi=phi}
    else {
      X2 <- sum(residuals(phi, type = "pearson")^2)
      
      
      # divide by the residual degrees of freedom
      phi <- X2/phi$df.residual
    }}
  # can also calculate with residual deviance
  print(phi)
  if(is.null(pretend)){pretend=TRUE}
  if (is.null(names)==FALSE){names = names[2:length(names)]}  
  if (is.null(names)==TRUE){names = paste("m",1:length(mod),sep="")}  
  Model   = 1:length(mod)
  LogLik     = vector(length = length(mod))
  ll      = vector(length = length(mod))
  n       = vector(length = length(mod))
  p       = vector(length = length(mod))
  AICc    = vector(length = length(mod))
  AIC     = vector(length = length(mod))
  RootMSE = vector(length = length(mod))
  
  
  
  # Make sure all models in list are either glm or lme4 objects. You can't compare mixed and fixed effects models.  
  allright=FALSE
  cl = character(length=length(mod))
  for (ii in 1:length(mod)){
    cl[ii] = class(mod[[ii]])[1] # identify the class of each model object in the list 
  }
  if (all(cl=="nlme") | all(cl=="nls") | all(cl=="gam") | all(cl=="betareg")| all(cl=="mer"|cl=="glm") | all(cl=="clmm" | cl=='sclm')) {allright=TRUE}

  
  if (allright==TRUE){
    # loop over the models in the list to extract relevant info.
    for (m in 1:length(mod)) {
      LogLik[m]      = logLik(mod[[m]])
      ll[m]      = as.numeric(LogLik[m])
      p[m]      = attr(logLik(mod[[m]]),"df")
      
      if (cl[m]=="mer"){
        r         = mod[[m]]@y - fitted(mod[[m]])} # get y from lme4 object
      
      if (cl[m]=="clmm"|cl[m]=="sclm"){
        # can't calculate residual variance for clmm models, so set to 0
        r         = rep(0,dim(mod[[m]]$model[1])[1])} 
      
      if  (cl[m] %in% c("glm","gam","betareg")) {
        r       = mod[[m]]$y - fitted(mod[[m]])}
      
      if (cl[m]=="nlme") {
        r       = mod[[m]]$residuals[,1]}  # get r from nlme object
      
      if (cl[m]=="nls") {
        r       = as.numeric(resid(mod[[m]]))}  # get r from nls object
      
      
      # calculate RMSE for all but clmm models
      RootMSE[m]= sqrt(sum(r^2))
      if (cl[m]=="clmm"|cl[m]=="sclm"){RootMSE[m]=NA}
      n[m] = length(r)
      if (is.null(phi)){
        AICc[m]   = as.numeric(-2 * ll[m] + 2*p[m] + 2*p[m]*(p[m] + 1)/(n[m] - p[m] - 1))
        AIC[m]    = as.numeric(-2 * ll[m] + 2*p[m])
      }
      else{
        if (is.null(phi)==FALSE){
          AICc[m]   = as.numeric(-2 * ll[m]/phi + 2*p[m] + 2*p[m]*(p[m] + 1)/(n[m] - p[m] - 1))
          AIC[m]    = as.numeric(-2 * ll[m]/phi + 2*p[m])
        }
      }
    }
    
    ###############################################################################
    # try to identify pretending models
    # calcualte all pairwise delta AIC values so we can identify pairs of models with delta AIC approximately     twice the difference in their number of parameters.
    
    daic = matrix(0,length(Model),length(Model))
    dll  = matrix(0,length(Model),length(Model))
    llDir  = matrix(0,length(Model),length(Model))
    dp   = matrix(0,length(Model),length(Model))
    for (ii in 1:length(Model)){
      for (iii in 1:length(Model)){
        dll[ii,iii] = ll[ii]-ll[iii]
        llDir[ii,iii] = ll[ii]>ll[iii]
        daic[ii,iii] = AIC[ii]-AIC[iii]
        dp[ii,iii]   = p[ii]-p[iii]
      }
    }
    
    # identify model pairs with close log likelihood values
    sameLL = dll>0 & dll<=0.5
    
    # identify model pairs whose difference in the number of parameters is roughly divisible by 2, which is the per-parameter penalty used in calculating AIC.  
    paramDif = (1 - daic/(dp*2))<0.2 & (1 - daic/(dp*2))>0
    
    # identify model pairs that meet both conditions. The column index should be the 'real' model, and the row index is the column;
    impostors = which(sameLL & paramDif,arr.ind=TRUE)
    
    
    delAIC = AICc-min(AICc)                      # Delta AICc
    W = exp(-0.5*delAIC)/sum(exp(-0.5*delAIC))   # Akaike Weight
    Wp = rep(0,length(Model))
    Wp[-impostors[,1]] = exp(-0.5*delAIC[-impostors[,1]])/sum(exp(-0.5*delAIC[-impostors[,1]]))   # Akaike Weight
    
    Pretending = character(length(Model))
    for (ii in 1:length(Model)){
      if(any(impostors[,2]==ii)){
        if(is.null(names)){getImpostors = as.character((c(impostors[impostors[,2]==ii,1])))}
        if(is.null(names)==FALSE){getImpostors = names[(c(impostors[impostors[,2]==ii,1]))]}
        Pretending[ii] = paste(getImpostors,collapse=", ") }}
    
    idx = sort(delAIC,index.return=TRUE)         # create index to sort by deltaAICc
    
    # Sort variables by index to output to table
    if (is.null(names)==TRUE){Model = Model[idx$ix]}  # model id number
    if (is.null(names)==FALSE){Model = names[idx$ix]} # model name if available
    LogLik      = formatC(LogLik[idx$ix],2,format="f")   # log likelihood
    p        = p[idx$ix]                           # number of parameters
    AICc     = formatC(AICc[idx$ix],2,format="f")  # AICc or QAICc
    RootMSE  = RootMSE[idx$ix]                     # RMSE - a measure of variance explained
    delAICc  = formatC(delAIC[idx$ix],2,format="f")# delta AICc or QAICc
    W        = formatC(W[idx$ix],3,format="f")     # Akaike weights
    Wp       = formatC(Wp[idx$ix],3,format="f")     # Akaike weights without pretending models
    Pretending= Pretending[idx$ix]
    
    # make table withouth phi
    if (is.null(phi)){
      if(pretend){modelTable = data.frame(Model,LogLik,n,p,AICc,delAICc,W,RootMSE,Wp,Pretending)}
      else{if (pretend==FALSE){modelTable = data.frame(Model,LogLik,n,p,AICc,delAICc,W,RootMSE)}}}
    
    # make table with phi (if dispersion parameter is supplied)
    if (is.null(phi)==FALSE){
      QAICc = AICc
      delQAICc = delAICc;
      if (pretend){modelTable = data.frame(Model,LogLik,n,p,QAICc,delQAICc,W,RootMSE,Wp,Pretending)}
      else{if (pretend==FALSE){modelTable = data.frame(Model,LogLik,n,p,QAICc,delQAICc,W,RootMSE)}}
    }
    modelTable # return table
  } else {
    warning("All models must be either glm or lme4 objects.",call=TRUE)
  }
}
```


### Import data:
```{r import data}
#use relevant working directory


# gleaner_universe_r_7_19_19 <- read_excel("~/Dropbox/GLEANER UNIVERSE STUDY/data sheets/gleaner_universe_r_7.19.19.xlsx", 
#     na = "NA")

# g_u <- gleaner_universe_r_8_15_22



g_u <- read.csv("https://raw.githubusercontent.com/maydixon/katydids/master/gleaner_universe_r_08.15.22_github.csv", sep=",", header=TRUE, stringsAsFactors = F )


colnames(g_u)
str(g_u)


# Call_analysis_avgs_R <- read_excel("~/Dropbox/GLEANER UNIVERSE STUDY/data sheets/Call_analysis_avgs_R.xlsx", 
# +     col_types = c("text", "numeric", "numeric", 
# +         "numeric", "numeric", "numeric", 
# +         "numeric", "numeric", "text", "text", 
# +         "text", "text", "text", "text", "numeric", 
# +         "text"))


check_1 <- g_u %>%
      group_by(Playback) %>%
      summarize(n=n())
##delete

```

### Guide to Columns: 
Species = Bat species abbreviations   
Species_full = Full bat species names   
ID: Bat ID   
Sex = (duh)   
Date = date
Set = Which suite of calls was used (Set 1- 4)   
Attempt = If we needed to repeat the trials again for some reason, could be 1 and 2   
Playback = the trial sound played   
Number = Order of playback 1-21, any extra redo trials at the end   
Reviewed: mostly unused bc I added it after most reviews, but in theory whether trial was checked over or not    
exclude: trial shouldn't be included in analysis (bc extra, redo, etc- see note)   
Then a bunch of call parameters:    
call_duration   
"peak_freq"   
"min_freq"   
"max_freq"   
"bandw" = bandwidth   
"entropy"   
"peaks"    
"pulses_call" = n pulses in a call   
"calls_callgroup"   
"sum_pulse_duration_callgroup"   
"duration_callgroup"   
"call_rate_used"   - s between the start of a call to the start of the next
"duty_cycle"   
"file_time_with_sound" = total amount of playback with sound   


### Check and clean data
```{r data cleaning, include =FALSE}
colnames(g_u)

#filter by unique species, unique bat names, unique scores, etc. 

sapply(g_u, unique) # applies "unique" function to all the columns in the dataset, gives all the unique values for each


#Fix mis-entered "D. gigliotosi " values: 
g_u <- g_u %>%
      mutate(Playback = replace(Playback, Playback =="D. gigliotosi ", "D. gigliotosi")) %>%
      mutate(Playback = replace(Playback, Playback =="Anaxipha sp. ", "Anaxipha sp."))


#sex has M, F, "M?" and "NA"
g_u %>% select(Sex) %>% unique() 

g_u %>% filter(Sex %in% c("M?", NA)) %>% # pull weird sexes
      select(ID, Sex) %>% # pull IDs with their sex
      unique #show the unique values

# lamp brac 1 - sex not noted - leave as NA
# 7 - blankie - sex not noted- leave as NA

# checked original datasheet for midnight cowboy, lists as "male", changing "M?" to "M"
g_u <- g_u %>% mutate(Sex = replace(Sex, ID== "Loph_silv_5 / Midnight Cowboy", "M"))



# Set has unknowns
g_u %>% select(Set) %>% unique() 
g_u %>% group_by(Set) %>% summarize (n= n()) 

g_u %>% filter(!Set %in% c(1:4))
#number has a lot of weird values, from extra trials- to include or no, depends on trial

# To dos:
# convert time into real times? - low priority, not that important
# plot call duration and other acoustic values to find out how well automatic classification did 
# double check for data duplications by seeing if any two bats' responses exactly match

```


### Code "call types"  like "katydid" and "cicada"
```{r add call categories}
#Recode a variable with the categories

g_u<- g_u %>% mutate(Call_type = if_else(Playback %in% c("A. spatulata","C. wheeleri","D. gigliotosi" ,"T. subfalcata","V. zederstedi"), "Katydid", 
      if_else(Playback %in% c( "Acla sp.","Aclodes sp.",  "Anaxipha sp."), "Cricket", 
      if_else(Playback %in% c("D. diastema", "D. ebraccatus", "H. fleishmanni", "P. pustulosus" ,"S. sila"), "Frog", 
      if_else(Playback %in% c("Q. gigas", "Z. smaragdina"), "Cicada", 
      if_else(Playback %in% c( "H. frenatus","T. rapicauda" ), "Gecko", 
      if_else(Playback %in% c("Beetle flight", "Frog hopping" , "Mouse rustles", "Moth sounds" ),"Movement cue", 
      if_else(Playback %in% c("White noise"), "White noise","Other"
      
      ))))))))


#order factor
g_u$Call_type<- factor(g_u$Call_type, levels = c( "Cricket" , "Katydid", "Cicada" , "Frog"  ,"Gecko", "Movement cue",    "White noise" ), ordered = TRUE )

unique(g_u$Call_type)


```

*Note* Moth sounds were only played to a few bats, should be removed for some analyses

```{r filter odd variables, include = FALSE }
#exploring data, organizing
# unique(g_u$Species)
# unique(g_u$Species_full)
# unique(g_u$Playback)
# class(g_u$Playback)
# unique(g_u$Response)
# class(g_u$Response) 

## remove moth sounds for now
g_u_all <- g_u

g_u <- subset(g_u, g_u$Playback!= "Moth sounds") 

#remove NAs 
g_u <- subset(g_u, g_u$Playback!="NA") 

## Just for now remove n= 1s: Micronycteris schmidtorum, glyphonycteris
#g_u <- subset(g_u, g_u$Species!="Micr_schm" & g_u$Species!="Glyp_davi") 

# use if no moth sounds
g_u$Playback<- factor(g_u$Playback, levels = c( "Acla sp.", #crickets
                                                "Aclodes sp." ,
                                                "Anaxipha sp.",
                                                "A. spatulata" , #katydids
                                                "T. subfalcata",
                                                "V. zederstedi" ,
                                                "C. wheeleri" ,
                                                "D. gigliotosi"  ,
                                                "Q. gigas" ,    #cicadas
                                                "Z. smaragdina"  ,
                                                "D. diastema" ,   #frogs
                                                "H. fleishmanni",
                                                "D. ebraccatus" ,
                                                "S. sila"     ,
                                                "P. pustulosus" ,
                                                "H. frenatus" ,   #geckos
                                                "T. rapicauda"  ,
                                                "Beetle flight",   # movement sounds
                                                "Frog hopping"  ,
                                                "Mouse rustles",
                                                "White noise"),   #white noise
                      ordered = TRUE )

#Use if moth sounds are included
# g_u$Playback<- factor(g_u$Playback, levels = c( "Acla sp."       ,     "Aclodes sp."   ,  "Anaxipha sp.", "A. spatulata" , "T. subfalcata", "V. zederstedi"  ,  "C. wheeleri" ,  "D. gigliotosi"  , "Q. gigas" ,  "Z. smaragdina"   ,
#         "D. diastema" , "H. fleishmanni", "D. ebraccatus" ,  "S. sila"     ,      "P. pustulosus" ,  "H. frenatus" , "T. rapicauda"  ,
#     "Beetle flight",  "Moth sounds", "Frog hopping"  , "Mouse rustles", "White noise"), ordered = TRUE )
```

### Add playback amplitudes for the diff categories
```{r add amplitudes, include = TRUE}
#####
# adding in amplitude
#####
g_u<- g_u %>% mutate(amplitude = case_when(
      Call_type == "Katydid" ~ 86.8, 
      Call_type == "Frog" ~ 75,
      Call_type == "Gecko" ~ 76.07,
      Call_type == "Cricket" ~ 70.22,
      Call_type == "Cicada" ~ 83.07,
      Playback == "Beetle flight" ~ 41.52,
      Playback == "Frog hopping"~ 39.52,
      Playback == "Mouse rustles" ~ 37.66,
      Playback == "White noise" ~ 75))

```

### Shorten bat species names
```{r shortened bat species names}

g_u <- g_u %>% mutate(Species_short = case_when(
      Species_full == "Artibeus jamaicensis" ~ "A. jamaicensis", 
      Species_full == "Gardnerycteris crenulatum" ~ "Ga. crenulatum",
      Species_full == "Glyphonycteris daviesi" ~ "Gl. daviesi",
      Species_full == "Lampronycteris brachiotis" ~ "La. brachiotis",
      Species_full == "Lonchorina aurita" ~ "Lon. aurita",
      Species_full == "Lophostoma brasiliense"  ~ "Lop. brasiliense" ,
      Species_full == "Lophostoma silvicolum" ~ "Lop. silvicolum",
      Species_full == "Micronycteris hirsuta" ~ "M. hirsuta",
      Species_full == "Micronycteris microtis" ~ "M. microtis",
      Species_full == "Micronycteris schmidtorum" ~ "M. schmidtorum",
      Species_full == "Phyllostomus discolor" ~ "P. discolor",
      Species_full == "Phyllostomus hastatus" ~ "P. hastatus",
      Species_full == "Tonatia saurophila" ~ "To. saurophila",
      Species_full == "Trachops cirrhosus" ~ "Tra. cirrhosus",
      Species_full == "Trinycteris nicefori"  ~ "Tri. nicefori" ))

g_u <-  g_u %>% relocate(Species_short, .after = Species_full) #move column next to other species columns


```

### Original response scale:

0 - no response  
1 - ears twitch in time with call  
2 - orients toward sound when playing  
3- flies towards speaker  
4 - hovers within .5 m  
5- lands on speaker  

Recode response with 0, 1, 4, 5, -\> Make a column that codes whether bats:
0 - (did nothing (0),   
1- ear twitched or came closer(1-3),  
4- approached within a half meter (4),  
5- or landed (5).  
(collapses 1-3, these distinctions may not be important/ espcalatory across spp.)  

Also make a binary column that just codes whether or not a bat landed. -\>   
or 0, 1, 2-3,4,5. With the idea that orient and comes closer can be conflated.

```{r recode responses}
#Recode a variable with 0, 1, 4, 5 

#g_u<- g_u %>% mutate(Response_ApproachLand = if_else(Response %in% c("0","1","2" ,"3"), "0", if_else(Playback %in% c("4"), "4", if_else(Response %in%c("5"),"5", "other"))))

g_u <- g_u %>% mutate(Response_ApproachLand = case_when(
      Response == 0 ~ 0, 
      Response == 1 ~ 1,
      Response == 2 ~ 1,
      Response == 3 ~ 1,
      Response == 4 ~ 4, 
      Response == 5 ~ 5))

g_u <- g_u %>% mutate(Response_Land = case_when(
      Response == 0 ~ 0, 
      Response == 1 ~ 0,
      Response == 2 ~ 0,
      Response == 3 ~ 0,
      Response == 4 ~ 0, 
      Response == 5 ~ 1))

```


### Palettes for plots
```{r palettes, include = TRUE}
#theme: 
TM <- theme_calc(base_size = 25) + theme(axis.text.x = element_text(angle = 45, hjust=1), plot.background =element_blank(), legend.title = element_blank()) #tilted x-axis labels and title, no legend title

TM2<-theme_calc(base_size = 25) + theme(axis.text.x = element_text(angle = 45, hjust=1), axis.title.x=element_blank()) #tilted x-axis labels, no x title

TM2.5<-theme_calc(base_size = 25) + theme(axis.text.x = element_text(angle = 45, hjust=1), axis.title.x=element_blank(), legend.position="none") #tilted x-axis labels, no x title


TM4<-theme_calc(base_size = 25) + theme(axis.text.x = element_text(angle = 45, hjust=1), axis.title.x=element_blank(), legend.position="none") #tilted x-axis labels, no x title, no legend


TM1 <- theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), legend.title = element_blank(), plot.background =element_blank() ) #blank axes, blank legend title

TM3 <-  theme_calc() +theme(axis.title.x=element_blank(), axis.text.x = element_text(angle = 75, hjust=1), legend.position = "none") #tilted x-axis labels and title, for no size control, remoe base_size argument #for diagonal text, put angle = 45

TM4 <-  theme_calc() +theme(axis.title.x=element_blank(), axis.text.x=element_blank(), legend.position = "none") # no size control, no x axis labels

n_colors<- length(unique(g_u$Species_full))
#this is the number of species in the plot/ dataset at any given time, can be used to change the palette

PL <-  "Spectral"
PL <- colorRampPalette(brewer.pal(n_colors, "Set3"))
PL = colorRampPalette(brewer.pal(11, "Spectral"))

#palette with a lot of colors
c25 <- c("dodgerblue2","#E31A1C", # red
                "green4",
                "#6A3D9A", # purple
                "#FF7F00", # orange
                "black","gold1",
                "skyblue2","#FB9A99", # lt pink
                "palegreen2",
                "#CAB2D6", # lt purple
                "#FDBF6F", # lt orange
                "gray70", "khaki2",
                "maroon","orchid1","deeppink1","blue1","steelblue4",
                "darkturquoise","green1","yellow4","yellow3",
                "darkorange4","brown")
pie(rep(1,25), col=c25)


# dark theme: 
dark_theme<- theme(panel.grid.major = element_line(colour = "darkgrey"),
             panel.grid.minor =  element_blank(),
             panel.background = element_rect(fill = 'black'),
             axis.line = element_line(colour = "white"),
             text = element_text(color = "white"), 
             plot.background= element_rect(fill = 'black'), #black background
             #legend.position = "none",
             axis.text.x = element_text(angle = 45, hjust=1, face = "italic"),
             axis.text = element_text(size = 16, color = "white"),
             axis.title = element_text(size = 16)  ) 

dark_theme_noline <- 
      theme(panel.grid.major = element_blank(), panel.grid.minor =  element_blank(),
       panel.background = element_rect(fill = 'black'),
       axis.line = element_line(colour = "white"),
       text = element_text(color = "white"), 
       plot.background= element_rect(fill = 'black'),

       legend.position = "none", axis.text.x = element_text(angle = 63, hjust=1, face = "italic"), axis.text =                   element_text(size = 16, color = "white"), axis.title = element_text(size = 16),  )   #gets rid of                    background
      
#+ theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), legend.position = "none") #format x-axis, and remove side legend #hjust 1 aligns labels
```

### Palette for coloring by Call_type
```{r Call_type Palette}

# Create a custom color scale (using RColorBrewer)
library(RColorBrewer)
CallCatColors <- brewer.pal(7,"Set1")

# Palette rearranged
#CallCatColors <- c("#984EA3", "#4DAF4A", "#377EB8", "#FF7F00", "#E41A1C", "#FFFF33", "#A6A6A6") 

# Alternative palette (OG powerpoint scheme)
CallCatColors <- c("#2A769E",  "#4D6123" , "#1E846A" , "#D0892C" , "#973721", "#573AA2" , "#A3A3A3"  )

#Alternative palette 2 (modified powerpoint scheme)
#CallCatColors <- c("#FDE84C", "#4D6123", "#19657E", "#EE964B", "#8C2635", "#6D3A47", "#A6A6A6")

# View palette
pie(rep(1,7), col=CallCatColors )
names(CallCatColors) <- levels(g_u$Call_type)
colScale_CallCat <- scale_fill_manual(name = "Call_type", values = CallCatColors)
colScale_color_CallCat <- scale_color_manual(name = "Call_type", values = CallCatColors)
#and then add the color scale onto the plot as needed


```

### Palette for plotting subsets
```{r plotting subsets}
  #### settings for plot type 3####
  G3<- geom_point(position = position_jitter(width = 0.05), size = 5)
  C3 <- coord_cartesian(ylim = c(0, 5.25))
  Plt2<-scale_colour_manual(values = PL(n_colors))
  Xlab2 <-  xlab("Acoustic stimuli")
  Ylab2 <-  ylab("Response score")
  Ylab3 <-  ylab(" Average response score")
  H2 <- 5  #height for plot output default
  W2<- 13 # height default
  
  # "#9E0142" "#CB334C" "#E95D47" "#F88D51" "#FDBE6E" "#FEE593" "#FFFFBF" "#EAF69E" "#BEE5A0" "#88CFA4" "#54AEAC" "#397EB8" "#5E4FA2"
  
   #Colors for graphs
cAJ<- scale_colour_manual(values = c("#9E0142")) #"#9E0142"
cGC<- scale_colour_manual(values = c("#CB334C"))
cLaB <- scale_colour_manual(values = c("#E95D47"))
cLA <- scale_colour_manual(values = c("#F88D51"))
cLoB <- scale_colour_manual(values = c("#FDBE6E"))
 cLS <- scale_colour_manual(values = c("#FEE593")) 
 cMH <- scale_colour_manual(values = c("#FFFFBF"))
 cMM <- scale_colour_manual(values = c("#EAF69E" ))
 cPH <- scale_colour_manual(values = c("#BEE5A0" ))
 cTS <-scale_colour_manual(values = c("#88CFA4" ))
 cTC <- scale_colour_manual(values = c("#54AEAC"))
 cTN <-scale_colour_manual(values = c("#397EB8"))
 cGD <-scale_colour_manual(values = c("#5E4FA2"))
 # "#5E4FA2"
 
 W3<- 19 #width
 H3<- 8  #height
```

### Organizing and exploring data 
- How many species do I have? 
- How many bats per species? 
- What is the sex of all the species? 
- (table with species, #, #m, #f) - How many playback exemplars per category?

```{r n per species, include = TRUE}
#summarize # of individuals per species
n_species <-g_u %>% group_by(Species_full) %>%
      summarise(N_total = n_distinct(ID, na.rm=TRUE), N_Female = length(unique(ID[Sex == 'F'])), N_Male = length(unique(ID[Sex == 'M']))) %>% arrange(desc(N_total))
n_species
#sum total n bats
total_n <- sum(n_species$N_total)
total_n

#write.csv(n_species, "n_species.csv")

```

### Data exploration - Which and how many bats species approach or land on potential prey sounds? 

*Which land?*

```{r species that landed, include = TRUE}
#Pulling out Species that land
land_sp <- g_u %>% filter(Response == 5) %>% select(Species_full, Playback, Call_type) 
land_sp 



#bats landed in 15 instances 
nrow(land_sp)

# these 5 bat species landed
unique(land_sp$Species_full)

#these 9 prey species were landed on
unique(land_sp$Playback)


 # plot of total lands and approaches by playback (outlines show which bat spp)

plot_byplayback <- function(RESPONSE= "5"){
  
   plot_playback <-   g_u %>%
       group_by(Call_type) %>%
       filter(Response >= RESPONSE) %>% 
       ggplot(aes( x= Playback)) +
            geom_bar( aes(fill = Call_type,  color = Species_short), na.rm= FALSE) + #color = "Species_short"
            scale_x_discrete(drop = FALSE) + #keep 0 levels
            #theme(axis.text.x = element_text(angle = 45, hjust=1)) + light theme
            dark_theme +
            theme(legend.background =  element_rect(fill = 'black'), #dark theme
                  legend.text = element_text(color = "white")) +
              ggtitle(ifelse(RESPONSE=="5", expression(paste("Number of bats that attacked each playback")), expression(paste("Number of bats that approached or attacked each playback"))))
   
 plot_playback   
}   

plot_byplayback(RESPONSE = "5")
#ggsave("plot_all lands by playback.pdf", width = 10, height = 7)

#plot of total lands by call_category
 plot_bytype <- function(RESPONSE = "5"){
  plot_type <- g_u %>%
       group_by(Call_type) %>%
       filter(Response >= RESPONSE) %>%
       ggplot(aes( x= Call_type)) +
            geom_bar( aes( fill = Playback)) +
             scale_x_discrete(drop = FALSE) + 
            #theme(axis.text.x = element_text(angle = 45, hjust=1)) +
            dark_theme +
            theme(legend.background =  element_rect(fill = 'black'),
                  legend.text = element_text(color = "white")) +
        
              ggtitle(ifelse(RESPONSE=="5", expression(paste("Number of bats that attacked each call type")), expression(paste("Number of bats that approached or attacked each call type")))) +
               xlab("Call category") +
               ylab("Count") 
  plot_type
 }
 plot_bytype(RESPONSE = "5")
#ggsave("plot_all lands by call type_narrow.pdf")
# THERE ARE 5 species HUNTING using sounds, for sure, hunting 9 things
```

*Data exploration - Which land or approach?*
```{r species that landed or approached}
# Species that land or approach

approach_land_sp <- g_u %>% filter(Response == 5 | Response == 4) %>% select("Species_short", "ID","Playback", "Call_type", "Response", "Notes")
approach_land_sp
nrow(approach_land_sp)
unique(approach_land_sp$Species_short)
unique(approach_land_sp$Playback)

 # 10 bat species approached or landed on at least one call, including A. jamaicensis (approached mouse rustles (predator inspection?): 
#  "A. jamaicensis"   "Ga. crenulatum"   "Gl. daviesi"      "Lon. aurita"      "Lop. brasiliense" "Lop. silvicolum"  "M. hirsuta"       "M. microtis"      "P. hastatus"      "Tra. cirrhosus"  

# 22 calls were approached: 
#  Mouse rustles  H. frenatus    H. fleishmanni P. pustulosus  D. ebraccatus  S. sila     Beetle flight  White noise    Moth sounds    Frog hopping   Q. gigas       C. wheeleri    A. spatulata   T. subfalcata  V. zederstedi  D. gigliotosi  Aclodes sp.    Anaxipha sp.   D. diastema    T. rapicauda   Acla sp.      



# table of how many times each call was approached or landed on 
n_app_land_playback<- g_u %>% 
      group_by(Playback) %>%
      summarize(n_applands = sum(Response >= 4))
n_app_land_playback   



#plot of total lands and approaches by playback (outlines show which bat spp)

plot_byplayback(RESPONSE = "4")

######
   ###         
  # this plot drops the category with no approaches (Z. smaragdina)
      g_u %>%
       group_by(Call_type) %>%
       filter(Response >=4) %>% 
       ggplot(aes( x= Playback)) +
            geom_bar( aes( fill = Species_short, position = 'dodge'), na.rm= FALSE) +
           # scale_x_discrete(drop = FALSE) + #keep 0 levels
            theme(axis.text.x = element_text(angle = 45, hjust=1)) +
          facet_grid(~ Call_type, drop = TRUE, space = 'free_x', scales = 'free_x', switch = 'x') +
          theme(panel.spacing.x = unit(0,"line"))  #keeps panels close
         # theme(strip.placement = 'outside')  # switch the facet strip label to outside 

### 



# number of times bats approached each *cue category*, and number of times controlled by opportunity (e.g., there were 5 katydid playbacks, but only 1 white noise)

n_app_land_cat<- g_u %>% group_by(Call_type) %>% summarize(n_applands = sum(Response >= 4), # n times each type approached or landed
      n_playbacks =n_distinct(Playback), # n playbacks in each category
      n_appland_playbacks = (sum(Response >= 4)/ (n_distinct(Playback))) #n apps/ lands to types when # playbacks/category (opportunities to approach category) is controlled
                                            )
n_app_land_cat

#plot of total lands and approaches by call_category
  plot_bytype(RESPONSE = "4") #plots all responses >4
#ggsave("plot_all lands and approaches by call type wide.pdf", width = 10, height = 7)

```

### plotting bat species mean responses to all sounds - which bats had the highest mean responses?

colored by which bat species landed: 
```{r  average bat responses to calls high to low}

# put n unique bats below X axis ticks? (not done)
#make light and dark versions
 

#base plot
p_avg_batspecies<- 
      g_u %>%
      mutate(Species_short = fct_reorder(Species_short, Response, .fun='mean')) %>% #reorders the columns from high to low mean response
      ggplot( aes(x=reorder(Species_short, -Response), y = Response), color = "black") + #the "-" orders it high to low color = "black" or "white" for dark or light mode
     # geom_violin() +
      geom_dotplot( aes(color = Call_type,
                        fill = Call_type ) ,
                   binaxis = "y",
                   stackdir = "center",
                   method = "histodot" , # fixed bin width dotdensity is default
                   binwidth =1/40, #max bin width - proportion of range of data
                   alpha = .7,
                   stackratio = 0.8, # doesn't  change dot size #.5 good for together plot
                    dotsize = 6 ,  #(previously not specified) #2 good for collective plot 12 good for single spp. plots
                   # width = .2
                   # right = TRUE
                  ) +
      # geom_point(size = 0.5, position = position_jitter(width = .3, height = 0), color = "lightgreen", alpha = 0.5) +
      coord_cartesian(ylim = c(0, 5)) + #standardize y axis
      
    
    theme(panel.grid.major = element_blank(), panel.grid.minor =  element_blank(),
       panel.background = element_rect(fill = 'white'),
       axis.line = element_line(colour = "black"),
       text = element_text(color = "black"),
       plot.background= element_rect(fill = 'white'),

       legend.position = "none", axis.text.x = element_text(angle = 63, hjust=1, face = "italic"), axis.text =                   element_text(size = 16, color = "black"), axis.title = element_text(size = 16),  )  + #gets rid of                    background
     # dark_theme_noline +

 xlab("Bat species") +
ylab("Response scores") +
ggtitle("Mean bat responses to all sounds")
      
# color points by if the bat landed

p_avg_batspecies_land <-  p_avg_batspecies +
        stat_summary(fun=mean, geom="point", shape=4, size=1, aes(color= as.factor(Response_Land)))  
p_avg_batspecies_land

#ggsave("Mean bat species responses to sounds by species_dark.jpg", width = 10, height = 7)

```


-  X Make function to plot out one playback species at a time (e.g. c.
    wheeleri), and to make a plot with each of them and to order them
    from highest mean response to lowest
 - X Make X. axes titles shorter (A. jamaicensis)
 -  make a variable for plot type? (light or dark theme) 
-  color plots by Call_type (category of call), or Response_Land (if a bat landed on (or approached) something) or
    if a bat is a known gleaner?
    - Add n's to x axis labels



## Plotting Bat  mean responses to each playback- 1 plot per playback: 
```{r plots - one plot per playback, median bat responses}

#Set up the plots  (alone it looks crazy but it is necessary to color the plots below by call_type
p_avg_batspecies_calltype <-  p_avg_batspecies + 
      stat_summary(fun=mean, geom="point", shape=4, size=2, aes(fill= Call_type)) + 
      colScale_CallCat +  #custom scale_fill_manual set outside
      colScale_color_CallCat
      
#Plot each, color is set by colScale_CallCat and previous plot
Playback_plots = g_u %>%
    group_by(Playback) %>%
    do(Playback_plots = p_avg_batspecies_calltype %+% . + #do applies fn to current group. here it applies  plot to each Playback
             #facet_wrap(~Playback) + #can use if you want facet labels instead of/with ggtitle
              ggtitle(paste("Bat responses to", unique(.$Playback))) + #makes title current group
             ggsave(filename = paste("bat_mean_responses_to_",unique(.$Playback),".pdf", sep = ""),
                    width = 177,
                    height = 100,
                    units = "mm" ) #85, 129, or 177 mm (1-3 columns) 
       ) 
        
Playback_plots$Playback_plots


```

## Are some sounds more attractive than others? Plots ranked by playback
-----
- this is going to be pulled by the different # of bats of different species. could deal with this in a few ways:
   - weight the average per bat species (account for there being more bats of some species than others. = (average response/ spp1) + (avg response/ spp2)…/ n species,
  -  Find the max bat response to each call species
	- Could "normalize" the bat reactions by subtracting the average AJ response from each avg spp response. 

   -Average responses might not be the best indicator- a bat could be a full on gleaner but be a specialist, only flying to one call. What about average MAXIMUM response to the calls per bat? (pull out the maximum response per each bat, get the average for the species. (Did the bats respond strongly to anything? That will pull out bats that responded strongly to something

   - a plot with some measure of difference from AJs: absolute difference in response from AJ mean response? 
-----   
   
plot with all bat responses, prey species on x, colored by whether a bat landed on a playback 
```{r}


############### violin plot #################
p_avg_preyspecies <- 
      g_u %>%
      filter(Call_type !="NA") %>%
      mutate(Playback = fct_reorder(Playback, Response, .fun='mean')) %>% #reorders the columns from high to low mean response
      ggplot( aes(x = reorder(Playback, -Response), y = Response)) + #the "-" orders it high to low #color = "black"
      geom_violin() +
      # geom_point(size = 0.5, position = position_jitter(width = .3, height = 0), color = "lightgreen", alpha = 0.5) +
      coord_cartesian(ylim = c(0, 5)) + #standardize y axis
    
    theme(panel.grid.major = element_blank(), panel.grid.minor =  element_blank(),
       panel.background = element_rect(fill = 'white'),
       axis.line = element_line(colour = "black"),
       text = element_text(color = "black"),
       plot.background= element_rect(fill = 'white'),
       legend.position = "none",
       axis.text.x = element_text(angle = 63, hjust=1, face = "italic"),
       axis.text = element_text(size = 16, color = "black"),
       axis.title = element_text(size = 16),  )  + #gets rid of  background
    #dark_theme_noline +
    xlab("Playback") +
    ylab("Response scores") +
    ggtitle("Mean bat responses to sounds")
```

test
```{r}

#### test code###
 test_fn <-function(ranked= TRUE) {
test <-      g_u %>%
                filter(Call_type !="NA") %>%
                filter(Species == "Trin_nice")  %>%
                 filter(Call_type !="NA") 

plot <-   test 

#reorders the x-axis from high to low mean response if response = TRUE
 if(ranked){
    plot <-   plot %>% mutate(Playback = fct_reorder(Playback, Response, .fun='mean')) %>%
          ggplot( aes(x = reorder(Playback, -Response), y = Response))  
    }else{
                plot <-   plot %>%
                      ggplot(aes(y=Response, x = Playback))
          }

    plot <- plot +
          geom_point() +
          theme(panel.grid.major = element_blank(),
                panel.grid.minor =  element_blank(),
                  panel.background = element_rect(fill = 'white'),
                  axis.line = element_line(colour = "black"),
                  text = element_text(color = "black", size = 10),
                  plot.title = element_text(face = "italic", size = 11),
                  legend.position = "right",
                  axis.title.x = element_blank(),
                  axis.text.x = element_text(angle = 63, hjust=1, face = "italic"),
                  axis.text = element_text( color = "black", size = 10), 
                  #axis.title = element_text(size = 16),  
                  )  
     

print(test)
print(plot)


} 
      test_fn(ranked= TRUE)         
#############
```

#bootstrapped means
```{r}

#Y= response, X= playback, within bat spp. boot_ci()

# store dataframes and plots in lists to be able to make a multiplot or grid object- see how plots look together 
# remove all the legends
#try making a multiplot situation (ggarrange from egg package, ?align_plots from the cowplot package?)
#make a version where X isn't reordered every time, so just one X on bottom,
#

#response score- 3 has so few data points- doesn't taper with more- combine 3 and 2?

#clean this up (get rid of excess lists and whatnot)





#pull unique species names
Spp <- unique(g_u$Species)

#initialize lists for plots and boot output


####fixes#####
# pull out ranked from function, test if function works on its own x
#try adding in lists, internally x
#check what output of mutate is
# maybe pull out x and y? response and playback? to make function more universal?
##############

#make plots and bootstrapped 95% cis for each bat

plot_bats <- function(d=d, ranked= TRUE) {
      
      #initialize lists for plots and boot output
      myplots <- list()
      bootsummary <- list()
      
        #loop through bat spp
        for (i in 1:length(Spp)) {
      
  #pull out one bat species at a time          
  data <-      d %>%
                filter(Call_type !="NA") %>%
                filter(Species ==Spp[i]) 
      
           #get bootstrapped means and 95% confidence intervals for the response to each playback
           Boot_sums <- boot_ci2(d = data, y = data$Response, x = data$Playback, perms = 5000, bca = F) %>%
                 rename(Playback = effect)
           
      #store bootsums in list     
          #  bootsummary[[i]] <- Boot_sums
      
      #make dotplot for bats       
     plot <-     data %>%
                 filter(Call_type !="NA") 
  
        
#reorders the x-axis from high to low mean response if ranked = TRUE
 if(ranked){
    plot <-   plot %>% mutate(Playback = fct_reorder(Playback, Response, .fun='mean')) %>%
          ggplot( aes(x = reorder(Playback, -Response), y = Response))  
    }else{
                plot <-   plot %>%
                      ggplot(aes(y=Response, x = Playback))
    }
     
     plot <- plot +
           geom_dotplot( aes(color = Call_type,
                              fill = Call_type ) ,
                         binaxis = "y",
                         stackdir = "center",
                         method = "histodot" , # fixed bin width dotdensity is default
                         binwidth =1/40, #max bin width - proportion of range of data
                         alpha = .7,
                         stackratio = 0.9, # doesn't  change dot size #.5 good for together plot
                          dotsize = 8 ,  #(previously not specified) #2 good for collective plot 12 good for single spp. plots
                         # width = .2
                         # right = TRUE
                        ) +
                        colScale_CallCat + # fill palette
                        colScale_color_CallCat + #color palette
              
            coord_cartesian(ylim = c(0, 5)) + #standardize y axis
          
          theme(panel.grid.major = element_blank(),
                panel.grid.minor =  element_blank(),
                  panel.background = element_rect(fill = 'white'),
                  axis.line = element_line(colour = "black"),
                  text = element_text(color = "black", size = 10),
                  plot.title = element_text(face = "italic", size = 11),
                  legend.position = "right",
                  axis.title.x = element_blank(),
                  axis.text.x = element_text(angle = 63, hjust=1, face = "italic"),
                  axis.text = element_text( color = "black", size = 10), 
                  #axis.title = element_text(size = 16),  
                  )  + 
          #dark_theme_noline +
          xlab("Playback") +
          ylab("Response scores") +
          ggtitle(paste(unique(data$Species_full)," (n = ", length(unique(data$ID)), ")", sep ="") )   #makes title current group, n is number of bats      
        
           if(length(unique(data$ID)) >=1){
                 plot = plot + geom_point(data = Boot_sums,
                                          aes( x= Playback,
                                               y = mean),
                                          color = "black",
                                          shape = 4,
                                          size = 1 )
           }
           
      #if more than n individuals, add bootstrapped 95% CI's to plot
          if(length(unique(data$ID)) >=7){
                plot = plot + geom_errorbar( data = Boot_sums,
                                aes( x=Playback,
                                     ymin = low,
                                     ymax =high,
                                     y = NULL ),
                                color = "black",
                                width=.2,
                                size=.25)
          }
          
      # #make pdfs of plots (85, 129, or 177 mm width to fit in 1-3 columns dimensions)            
                 plot = plot +   ggsave(filename = paste(ifelse(ranked,"", "unranked"), unique(data$Species_full), "responses_to_playbacks", ".jpg", sep = ""), width = 177, height = 55, units = "mm" )
                 
      #add plot to list           
      myplots[[i]] <- plot
      
      plot
      print(plot)
     # print(Boot_sums)
      }
}

plot_bats(d = g_u, ranked = FALSE)
#have to fix this

myplots

names(myplots) <- unique(g_u$Species)
names(bootsummary) <- unique(g_u$Species)
ggpubr::ggarrange(plotlist = myplots[1:8], ncol = 1, common.legend = TRUE)
align_plots(plotlist = myplots[1:8], align = "v" )
myplots$Trin_nice
ggsave("test_plot_allbats_long.jpg", width = 177, units = "mm", height = 800)
# library(ggpubr)
# library(egg)
# library(cowplot)





```


dot plot attempt
````{r dot plot attempt }
############### dot plot attempt ##############
### Right now the error bar thing doesn't work. I think I need to give up the "do" strategy and use a for loop or a function or apply to make the summary data by group and the plots at the same time.  
#make the bat species a list.
#subset data successively by each item in list
#make summary data from subsetted data, then return plot, named df with summary data. 



means <- g_u %>% 
      mutate(effect= paste(Species_short, Playback, sep="_")) %>% #this to make 1 line for each subset
      boot_ci2(d = ., y = .$Response, x = .$effect, perms = 5000, bca = F) %>%
      separate(effect, into=c('Species_short', 'Playback'), sep="_", remove=F) 



p_avg_preyspecies <- 
      g_u %>%
      filter(Call_type !="NA") %>%
      mutate(Playback = fct_reorder(Playback, Response, .fun='mean')) %>% #reorders the columns from high to low mean response
      ggplot( aes(x = reorder(Playback, -Response), y = Response)) + #the "-" orders it high to low #color = "black"
      geom_dotplot( aes(color = Call_type,
                        fill = Call_type ) ,
                   binaxis = "y",
                   stackdir = "center",
                   method = "histodot" , # fixed bin width dotdensity is default
                   binwidth =1/40, #max bin width - proportion of range of data
                   alpha = .7,
                   stackratio = 0.9, # doesn't  change dot size #.5 good for together plot
                    dotsize = 8 ,  #(previously not specified) #2 good for collective plot 12 good for single spp. plots
                   # width = .2
                   # right = TRUE
                  ) +
      colScale_CallCat + # palette
      colScale_color_CallCat +
       geom_point(data = Boot_sums, aes( x= Playback, y = mean, color = "black"), shape = 4, size =1 ) + 
         #  geom_errorbar( data = Boot_sums, aes( x= Playback, ymin = low, ymax = high, color = "black"), width=.1, size=1) +
      coord_cartesian(ylim = c(0, 5)) + #standardize y axis
    theme(panel.grid.major = element_blank(), panel.grid.minor =  element_blank(),
       panel.background = element_rect(fill = 'white'),
       axis.line = element_line(colour = "black"),
       text = element_text(color = "black"),
       plot.background= element_rect(fill = 'white'),
       legend.position = "none",
       axis.text.x = element_text(angle = 63, hjust=1, face = "italic"),
       axis.text = element_text( color = "black", size = 10), 
       #axis.title = element_text(size = 16),  
       )  + 
    #dark_theme_noline +
    xlab("Playback") +
    ylab("Response scores") +
    ggtitle("Mean bat responses to sounds")

p_avg_preyspecies
ggsave("aa_test_dotplot.jpg", width = 177, height = 50, units = "mm" )
################
      
# color points by if the bat landed
# p_avg_preyspecies_land <-  p_avg_preyspecies +
#         stat_summary(fun=mean, geom="point", shape=23, size=3, aes(fill= g_u$Response_Land)) +
#         ggtitle("Mean bat responses to sounds, gray = any bat landed ")
# 
# p_avg_preyspecies_land
#ggsave("Mean responses to sounds- gray equals any bat landed_dark.pdf")


##### RETURN HERE######
### Right now the error bar thing doesn't work. I think I need to give up the "do" strategy and use a for loop or a function or apply to make the summary data by group and the plots at the same time.  make the bat species a list. subset data successively by each item in list. make summary data from subsetted data, then return plot, named df with summary data. 




Bat_plots = g_u %>%
    group_by(Species_short) %>%
    do(Bat_plots = p_avg_preyspecies %+% . + #do applies fn to current group. here it applies  plot to each bat species
             #facet_wrap(~Species_full) + #can use if you want facet labels instead of labels with ggtitle
      stat_summary(fun=mean, geom="point", shape = 4, size = 1 ) +
      geom_errorbar(aes(data = subset(means, Species_short== .), ymin=low, ymax=high, width=.1), size=1)+      
       theme(legend.position = "none",
            plot.title = element_text(face = "italic", size = 11),
            text = element_text(size=10),
            axis.title.x = element_blank()) + #take out for            
      ggtitle(paste(unique(.$Species_full)," (n = ", length(unique(.$ID)), ")", sep ="") ) + #makes title current group, n is number of bats          
             ggsave(filename = paste(unique(.$Species_full),"responses_to_playbacks", ".jpg", sep = ""), width = 177, height = 55, units = "mm" ) #85, 129, or 177 mm (1-3 columns)  #height = ,
       ) 

```


plot with all bat responses, prey species on x, colored by call type 
```{r plot with all prey on X, all bats}
#Set up the plots  
p_avg_preyspecies_calltype <-  p_avg_preyspecies + 
      colScale_CallCat +
      stat_summary(fun=mean, geom="point", shape = 4, size = 1, aes(fill = Call_type) ) +
      colScale_CallCat + #custom scale_fill_manual set outside
      theme(legend.position = "right") + 
      theme(legend.background =  element_rect(fill = 'white'), #dark theme
                  legend.text = element_text(color ="black")) +
      labs( color = 'Sound category', fill = 'Sound category') #IDK why changing the legend title this doesn't work
p_avg_preyspecies_calltype
#ggsave("mean_responses_byplayback.pdf")

```
### plots with all prey on X, 1 plot per bat species, playbacks ranked by mean response
```{r plot with all prey on X, 1 plot per bat species}
#Plot each, color is set by colScale_CallCat in previous plot

######## TO DO DELETE #######
# add bootstraped  95% confidence intervals to plots with sifficient n
# bonus points if I only do that on plots with >n than ? (5?)
# maybe temporarily take out sumary diamonds. looks at plots without

#########################
Bat_plots = g_u %>%
    group_by(Species_full) %>%
    do(Bat_plots = p_avg_preyspecies_calltype %+% . + #do applies fn to current group. here it applies  plot to each Playback
             #facet_wrap(~Species_full) + #can use if you want facet labels instead of labels with ggtitle
      theme(legend.position = "none") + 
      ggtitle(paste(unique(.$Species_full)," responses to playbacks (n = ", length(unique(.$ID)), ")", sep ="") ) + #makes title current group, n is number of bats          
             ggsave(filename = paste(unique(.$Species_full),"responses_to_playbacks", ".jpg", sep = ""), width = 177, height = 50, units = "mm" ) #85, 129, or 177 mm (1-3 columns)  #height = ,
       ) 
Bat_plots$Bat_plots





```



```{r}
#Does playback or  bat species predict whether a bat approaches or lands? 
# recode response into binary- 0 or 1
#use whatever model works with binary data
# do model selection, or see whether model is significant, see which species are preferred
     
```


### D0 different bats have different preferences? 

 cumulative link mixed model
```{r did bats have different overall responses to playbacks?}
################ Can put this stat on chart: Different species respond to sounds differently

# Can remove bats with low sample sizes
# g_u <- g_u %>% filter(Species_full != "Glyphonycteris daviesi")
# g_u <- g_u %>% filter(Species_full != "Micronycteris schmidtorum")


# and remove the 'control' frugivores
#no AJS
g_u_2<- subset(g_u, g_u$Species != "Arti_jama")

# Do different bats overall have different responses to sounds?
# CLMM: Response score ~ Playback 


G_U_clmm_pl<- clmm(as.factor(Response) ~ Species_short + (1| ID), data= g_u)

#G_U_clmm_pl<- clmm(as.factor(Response) ~ Species + (1| Number) + (1| ID), data= g_u)
summary(G_U_clmm_pl)

#get estimated marginal mean responses per species
sp_em <-emmeans(G_U_clmm_pl, "Species_short")
sp_em
#sp_em_cld<- multcomp cld(sp_em, letters=LETTERS)
#sp_em_cld


#plot(sp_em)

#ggsave("emmeans_all_pl.jpg")

```

* To dos: 
add n's (n_species) to x axis ticks  
set emmean on response scale  
add emmeans to g_u then could plot raw data below??
#normalized bat responses to each prey species? subtracting AJ mean
response Get AJ mean/median responses to each call make wide with
species as columns make new column with spp-AJ

*Plot overall emmean responses of bats to calls, ranked by response, dark theme*
```{r emmeans total bat responses high to low}

#theme_set(theme_classic(), text = element_text(color = "white"))    

p_emmeans_batspecies<- 
      ggplot(as.data.frame(sp_em), aes(x=reorder(Species_short, -emmean), ymin=asymp.LCL,ymax=asymp.UCL, color = "darkgreen")) +
      geom_linerange(size = 4, color= "darkolivegreen4") +
      geom_point(aes(Species_short, emmean, size = 1), color = "darkolivegreen3") +
  
       theme(panel.grid.major = element_line(colour = "darkgrey"),
             panel.grid.minor =  element_blank(),
             panel.background = element_rect(fill = 'black'),
             axis.line = element_line(colour = "white"),
             text = element_text(color = "white"), 
             plot.background= element_rect(fill = 'black'),
             legend.position = "none",
             axis.text.x = element_text(angle = 63, hjust=1, face = "italic"),
             axis.text = element_text(size = 16, color = "white"),
             axis.title = element_text(size = 16),  )  + #gets rid of background

       xlab("Bat species") +
       ylab("Response score estimated marginal means") 
      

#### workspace, delete, trying to make X labels with N ###
# scale_x_discrete(  labels=c("location" = "location", "sound" = "sound", "smell" ="odor", "neither" = "control"))
# 
# ggtitle(ifelse(species=="AJ", expression(paste("Frugivorous ", italic("Artibeus jamaicensis"))), 
#                                   expression(paste("Predatory ", italic("Lophostoma silvicolum")))))+
#####


p_emmeans_batspecies
ggsave("p_emmeans_call_type.jpg", width = 10, height = 7)
```




### Do bats respond more overall to some categories compared to others?

cumulative link mixed model of how call type predicts response
```{r bat response to call categories}
# should add assumptions check

# CLMM: bat response ~ call type ( number )

unique(g_u$Call_type)

#choose random effects structure
clmm_call_type<- clmm(as.factor(Response) ~ Call_type + (1| ID), data= g_u)
clmm_call_type1<- clmm(as.factor(Response) ~ Call_type + (1| ID) + (1| Set), data= g_u)
rM<-rankModels(list(clmm_call_type, clmm_call_type1))
rM
#best to use both random effects

# estimated marginal mean responses by call type
em_call_type <-emmeans(clmm_call_type1, "Call_type")
em_call_type

# letter displays (problematic)
cld_call_type<- multcomp::cld(em_call_type, letters=LETTERS)
cld_call_type

## note from cld.emmGrid {emmeans} on compact letter displays (cld's): "We warn that such displays encourage a poor practice in interpreting significance tests. CLDs are misleading because they visually group means with comparisons P > alpha as though they are equal, when in fact we have only failed to prove that they differ. As alternatives, consider pwpp (graphical display of P values) or pwpm (matrix display)."


pwpm_call_type<- pwpm(em_call_type, letters=LETTERS) #experiment - letter displays
pwpm_call_type
pwpp_call_type<- pwpp(em_call_type, letters=LETTERS) #experiment
contrast(regrid(em_call_type)) #back transformed contrasts 


#plot(cld_call_type)
#ggsave("category_emmeans.jpg")
```
plot of estimated mean responses to call types
```{r}
theme_set(theme_classic())    
ggplot(as.data.frame(sp_em), aes(x=reorder(Species_short, -emmean), ymin=asymp.LCL,ymax=asymp.UCL, color = "darkgreen"))

p_emmeans_call_type<- ggplot(cld_call_type, aes(x = reorder(Call_type, -emmean),ymin=asymp.LCL,ymax=asymp.UCL)) + 
    geom_linerange(size = 1.5, color = "darkolivegreen4") +
    geom_point(aes(x = Call_type, y = emmean, size = 1), color ="darkolivegreen3", fill = "darkolivegreen3") +
    # theme(panel.grid.major = element_blank(), #light theme (can switch)
    #       panel.grid.minor =  element_blank(),
    #       panel.background = element_blank(),
    #       axis.line = element_line(colour = "black"),
    #       legend.position = "none",
    #       axis.text.x = element_text(angle = 45, hjust=1),
    #       axis.text = element_text(size = 16),
    #       axis.title = element_text(size = 16))  + #gets rid of background
    theme(panel.grid.major = element_line(colour = "darkgrey"),# dark theme
             panel.grid.minor =  element_blank(),
             panel.background = element_rect(fill = 'black'),
             axis.line = element_line(colour = "white"),
             text = element_text(color = "white"), 
             plot.background= element_rect(fill = 'black'),
             legend.position = "none",
             axis.text.x = element_text(angle = 45, hjust=1, face = "italic"), #angle = 63
             axis.text = element_text(size = 16, color = "white"),
             axis.title = element_text(size = 16),  )  + #gets rid of background  

    xlab("Call Category") +
    ylab("Response score estimated marginal means")
      
#geom_point(aes(cld_call_type$emmean, Call_type, colour = Call_type)) +

p_emmeans_call_type
#ggsave("p_emmeans_call_type.jpg", width = 8, height = 5)
```
This is likely including bats that aren't using sounds to hunt, and things that some species like and others do not will be relatively washed out. 

### Do bats approach or land on some categories more than others?
```{r}
# bat response ~ category ( number )

clm_AppLand_call_type<- clmm(as.factor(Response_ApproachLand) ~ Call_type + (1|ID) + (1|Set) , data= g_u)

summary(clm_AppLand_call_type)

em_AppLand_call_type <-emmeans(clm_AppLand_call_type, "Call_type")
em_AppLand_call_type
cld_AppLand_call_type<- multcomp::cld(em_AppLand_call_type, letters=LETTERS)
cld_AppLand_call_type
###
plot(em_AppLand_call_type)
class(em_AppLand_call_type)

 # m <- glmer(Response_land ~ Call_type + (1|ID) , data= g_u, family = binomial, control = glmerControl(optimizer = "bobyqa"), nAGQ = 10)

```
This doesn't seem quite right. 


### Acoustics

Look at acoustic parameters of the playbacks (currently the values are averages of each playback type, not unique the the exact call used in a given trial)
```{r acoustic database}
df_sounds <- g_u %>% 
      filter(Set == 1:4) %>%
      #pull out first column for each unqiue playback and set
      #distinct(Set, Playback, .keep_all = TRUE) %>%  #use when each set has different values
      distinct(Playback, .keep_all = TRUE) %>% #pull 1 per playback
      select(Playback,Set,  call_duration:amplitude) %>%
      #mutate(Playback_Set = paste(Playback, Set)) %>%
      relocate( Playback, Set, Call_type ) %>% mutate(call_duration = as.numeric(call_duration))



 df_sounds %>%
       pivot_longer(cols= "call_duration":"amplitude",
                    names_to = "sound_measurements",
                    values_to = "sound value",
                    values_ptypes = list(val = 'character')
                   ) %>%
       ggplot(aes(x = Playback)) +
      geom_point(aes(y=sound_value, color = Call_type)) +
      facet_wrap(~ sound_measurements, scales = "free_y") +
 
       #scale_y_continuous(trans='log10') +
       theme(axis.text.x = element_text(angle = 45, hjust=1)) 
       
 
 sounds_long <- df_sounds %>%
       pivot_longer(cols= "call_duration":"amplitude",
                    names_to = "sound_measurements",
                    values_to = "sound_value",
                    values_ptypes = list(val = 'character')
                   ) 
duty_cycle <-  sounds_long %>%
       filter(sound_measurements == "duty_cycle") %>%
       ggplot(aes(x = Playback)) +
      geom_point(aes( y= sound_value, color = Call_type)) +
       ylab("Duty cycle") +
       xlab("Playback") +
       theme(axis.text.x = element_text(angle = 45, hjust=1)) 
 duty_cycle
 ggsave("duty_cycle.pdf")
       

```
Common sense check: file time with sound and duty cycle should be pretty correlated. They might not be *perfectly* correlated because duty cycle is calculated with call groups, and some of the calls and call groups had some silence between the calls
```{r}
df_sounds %>%
      ggplot(aes(x = duty_cycle,
                 y = file_time_with_sound,
                 color = Call_type )) +
      geom_point()

# these should be pretty correlated
```




## Old plots - ignore
Response bat species average responses to different groups:((cant really
do averages on ordinal scales, but works for visualization))

```{r mean responses to call categories}
Resp_avg<-g_u %>% group_by(Species_full, Playback ) %>%
      summarise(Resp_average = mean(Response, na.rm=TRUE))
Resp_avg
```

```{r}
g_u_p <- ggplot(data = g_u, aes(x = Playback, y = Response, colour = Species_full))

g_u_p <- g_u_p + geom_point(position = position_jitter(width = 0.1), size = 5)
g_u_p <- g_u_p + coord_cartesian(ylim = c(0, 5.25))
g_u_p <- g_u_p + scale_colour_manual(values = PL(n_colors))
g_u_p <- g_u_p + TM2
g_u_p <- g_u_p +  xlab("Acoustic stimuli")
g_u_p <- g_u_p +  ylab("Response score") 

g_u_p


#ggsave("gleaner_universe_fulltemp.jpg", width = 19, height = 8)

```

```{r}
g_u_pl <- ggplot(data = g_u, aes(x = Playback, y = Response, colour = Species_full))

g_u_pl <- g_u_pl + geom_point(position = position_jitter(width = 0.05), size = 5)
g_u_pl <- g_u_pl + coord_cartesian(ylim = c(0, 5.25))
g_u_pl <- g_u_pl + scale_colour_manual(values = PL(n_colors))
g_u_pl <- g_u_pl + TM3 #can take out x legend line if I want, TM3 or TM4
g_u_pl <- g_u_pl +  xlab("Acoustic stimuli")
g_u_pl <- g_u_pl +  ylab("Response score") + facet_wrap(~ Species_full) #this makes a nice facet

g_u_pl
#ggsave("faceted_responses_Full_X.jpg", width = 12)

```

########################## 

########################## 

AVERAGES

```{r}
Resp_avg

g_u_p_avg <- ggplot(data = Resp_avg, aes(x = Playback, y = Resp_average, colour = Species_full))
g_u_p_avg  <- g_u_p_avg  + geom_point(size = 8)
#g_u_p_avg  <- g_u_p_avg  + geom_point(position = position_jitter(width = 0.1))
g_u_p <- g_u_p + coord_cartesian(ylim = c(0, 5.25))
g_u_p_avg <- g_u_p_avg + TM
g_u_p_avg <- g_u_p_avg + scale_colour_manual(values = PL(n_colors))
g_u_p_avg <- g_u_p_avg +  xlab("Acoustic stimuli")
g_u_p_avg <- g_u_p_avg +  ylab("Mean response score")
g_u_p_avg 

 #
 #ggsave("gleaner_universe_avgtemp.jpg",  height = 8 ,width = 19) 

#save with tilty text, save with 8 x 17 defaults
#save without x axis
```

No axes graph 1

```{r}

g_u_p_nax <- g_u_p + TM1

 #ggsave("gleaner_universe_full_NAX.jpg", width = 17, height = 8)



```

No axes graph 2

```{r}

g_u_p_avg_NAX  <- g_u_p_avg + TM1
g_u_p_avg_NAX

 #ggsave("gleaner_universe_avg_NAX.jpg", width = 17, height = 8)

#Saving 17 x 3.91 in image
```

##faceted
```{r}
head(Resp_avg)

g_u_p_avg_f <- ggplot(data = Resp_avg, aes(x = Playback, y = Resp_average, colour = Species_full))
g_u_p_avg_f  <- g_u_p_avg_f  + geom_point(size = 5)
#g_u_p_avg_f  <- g_u_p_avg_f  + geom_point(position = position_jitter(width = 0.1))
g_u_p <- g_u_p + coord_cartesian(ylim = c(0, 5.25))
g_u_p_avg_f <- g_u_p_avg_f + TM4
g_u_p_avg_f <- g_u_p_avg_f + scale_colour_manual(values = PL(n_colors))
g_u_p_avg_f <- g_u_p_avg_f +  xlab("Acoustic stimuli")
g_u_p_avg_f <- g_u_p_avg_f +  ylab("Mean response score")
g_u_p_avg_f  <- g_u_p_avg_f + facet_wrap(~ Species_full)
g_u_p_avg_f
 #
 #ggsave("gleaner_universe_avg_facet_noX.jpg", width = 11) # height = 8 ,width = 17) 

#save with tilty text, save with 8 x 17 defaults
#save without x axis
```

########################### 

########################### 

##SUBSETS##

The quick and dirty way to make color palette names [1] Art jam
"#9E0142" "#CB334C" "#E95D47" "#F88D51" "#FDBE6E" [6] "#FEE593"
"#FFFFBF" "#EAF69E" "#BEE5A0" "#88CFA4" [11] "#54AEAC" "#397EB8"
"#5E4FA2"

Trac Cirr PLOT with axes. use TM4 FOR NO AXES

```{r Trac Cirr}
g_u_p_TC <- ggplot(data = g_u[g_u$Species =="Trac_cirr",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_TC <- g_u_p_TC + G3 +C3 + TM3 + Xlab2 + Ylab2  +cTC
g_u_p_TC

#ggsave("gleaner_universe_TC.jpg", width = W3, height = H3)

#and TC's with AVERAGES


g_u_p_TC_a <- ggplot(data = Resp_avg[Resp_avg$Species_full =="Trachops cirrhosus",], aes(x = Playback, y = Resp_average, colour = Species_full))

g_u_p_TC_a <- g_u_p_TC_a + G3 +C3 + TM3 + Xlab2 + Ylab2  +cTC
g_u_p_TC_a

#ggsave("gleaner_universe_TC_avg.jpg",  width = W3, height = H3)

```

AJ PLOT with axes. use TM4 FOR NO AXES

```{r}
g_u_p_AJ <- ggplot(data = g_u[g_u$Species =="Arti_jama",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_AJ <- g_u_p_AJ + G3 +C3 + TM4 + Xlab2 + Ylab2  +cAJ
g_u_p_AJ

#ggsave("gleaner_universe_AJ.jpg", width = W3, height = H3)

#and AJ's with AVERAGES


g_u_p_AJ_a <- ggplot(data = Resp_avg[Resp_avg$Species_full =="Artibeus jamaicensis",], aes(x = Playback, y = Resp_average, colour = Species_full))

g_u_p_AJ_a <- g_u_p_AJ_a + G3 +C3 + TM4 + Xlab2 + Ylab2  +cAJ
g_u_p_AJ_a

#ggsave("gleaner_universe_AJ_avg.jpg", width = W3, height = H3)

```

AJ ALL GRAPH

```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT


g_u_p_AJ <- ggplot(data = g_u[g_u$Species =="Arti_jama",], aes(x = Playback, y = Response, colour = Species_full))
g_u_p_AJ <- g_u_p_AJ + G3 +  C3 + TM4 + Xlab2 + Ylab2  +cAJ + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Artibeus jamaicensis",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4) #parameters for the averages
     
g_u_p_AJ

#ggsave("gleaner_universe_AJ_a.jpg", width = W3, height = H3)

```

```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT




g_u_p_TC <- ggplot(data = g_u[g_u$Species =="Trac_cirr",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_TC <- g_u_p_TC + G3 +C3 + TM4 + Xlab2 + Ylab2  +cTC + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Trachops cirrhosus",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_TC

#ggsave("gleaner_universe_TC_a.jpg", width = W3, height = H3)


```

```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT


g_u_p_LS <- ggplot(data = g_u[g_u$Species =="Loph_silv",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_LS <- g_u_p_LS + G3 +C3 + TM3 + Xlab2 + Ylab2  +cLS + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lophostoma silvicolum",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_LS

##ggsave("gleaner_universe_LS_a.jpg", width = W3, height = H3)


```

LOPH BRASILIENSE

```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT

g_u_p_LoB <- ggplot(data = g_u[g_u$Species =="Loph_bras",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_LoB <- g_u_p_LoB + G3 +C3 + TM3 + Xlab2 + Ylab2  +cLoB + #all parameters for general data
       dark_theme +
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lophostoma brasiliense",], mapping=aes(x = Playback, y = Resp_average), color = "white", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_LoB





g_u_p_LoB <-
      g_u %>%
      filter(Species == "Loph_bras") %>%
      mutate(Playback = fct_reorder(Playback, Response, .fun='mean')) %>%

      ggplot( aes(x = Playback, y = Response, colour = Species_full))

g_u_p_LoB <- g_u_p_LoB + G3 +C3 + TM3 + Xlab2 + Ylab2  +cLoB + #all parameters for general data
       dark_theme +
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lophostoma brasiliense",], mapping=aes(x = Playback, y = Resp_average), color = "white", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_LoB

#ggsave("gleaner_universe_LoB_a_dark.jpg", width = W3, height = H3)


```

PHYLLOSTOMUS HASTATUS

```{r}

g_u_p_PH <- ggplot(data = g_u[g_u$Species =="Phyl_hast",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_PH <- g_u_p_PH + G3 +C3 + TM4 + Xlab2 + Ylab2  +cPH + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Phyllostomus hastatus",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_PH

#ggsave("gleaner_universe_PH_a.jpg", width = W3, height = H3)

```

Lampronycteris brachiotis

```{r, eval = FALSE}

g_u_p_LaB <- ggplot(data = g_u[g_u$Species =="Lamp_brach",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_LaB <- g_u_p_LaB + G3 +C3 + TM4 + Xlab2 + Ylab2  +cLaB + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lampronycteris brachiotis",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_LaB

#ggsave("gleaner_universe_LaB_a.jpg", width = W3, height = H3)


```

Trinycteris nicefori

```{r, eval= FALSE}

g_u_p_Trn <- ggplot(data = g_u[g_u$Species =="Trin_nice",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_Trn <- g_u_p_Trn + G3 +C3 + TM4 + Xlab2 + Ylab2  +cLaB + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Trinycteris nicefori",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_Trn
#rm(g_u_p_Trn)
#ggsave("gleaner_universe_Trn_a.jpg", width = W3, height = H3)


```

Lonchorina aurita

```{r}

g_u_p_Loa <- ggplot(data = g_u[g_u$Species =="Lonc_auri",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_Loa <- g_u_p_Loa + G3 +C3 + TM3 + Xlab2 + Ylab2  +cLA + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lonchorina aurita",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_Loa
#rm(g_u_p_Loa)
#ggsave("gleaner_universe_Loa_b.jpg", width = 9, height = H2)
#5 13

```

Glyphonycteris daviesi
```{r Glyp davi}

g_u_p_Gld <- ggplot(data = g_u[g_u$Species =="Glyp_davi",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_Gld <- g_u_p_Gld + geom_point(size=5) +C3 + TM2.5 + Xlab2 + Ylab2  + cGD + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Glyphonycteris daviesi",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_Gld
#rm(g_u_p_Gld)
ggsave("gleaner_universe_Glyphdavi.jpg", width = 9, height = H2)
#5 13

```

```{r Gard cren}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT




g_u_p_GC <- ggplot(data = g_u[g_u$Species =="Gard_cren",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_GC <- g_u_p_GC + G3 +C3 + TM4 + Xlab2 + Ylab2  +cGC + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Gardnerycteris crenulatum",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_GC

#ggsave("gleaner_universe_GC_a.jpg", width = 9, height = H2)


```

## generalizable p1 and p2 things

```{r}

###settings for plot type 1###
  G1<- geom_point(size = 5) 
  G <- geom_point( size = 5, position = position_jitter(width = 0.1))
  C <- coord_cartesian(ylim =c(0, 5.25)) 
  Plt<-scale_colour_manual(values = PL(n_colors))
  Xlab1 <-  xlab("Acoustic stimuli")
  Ylab1 <-  ylab("Response score")
  FW <- facet_wrap(~ Species_full)
  
  #### plot 2####
  G2 <- geom_point()
  GG2 <- geom_point(position = position_jitter(width = 0.1), size = 3)
  C2 <- coord_cartesian(ylim = c(0, 5.25))
  Plt2<-scale_colour_manual(values = PL(n_colors))
  Xlab2 <-  xlab("Acoustic stimuli")
  Ylab2 <-  ylab("Response score")
  FW2<- facet_wrap(~ Playback) #ncol controls the number of columns, could easily be 2
  H2 <- 5  #height for plot output default
  W2<- 13 # height default
  
```

## Cicadas

cicada plot 1

```{r}
cicada <- subset( g_u, g_u$Playback == "Q. gigas" | g_u$Playback == "Z. smaragdina")

cicada_p_1 <- ggplot(data = cicada, aes(x = Playback, y = Response, colour = Species_full))
#cicada_p_1  <- cicada_p_1    #geom_point(size = 5) 
cicada_p_1  <- cicada_p_1  + G   #geom_point(position = position_jitter(width = 0.1))
cicada_p_1 <- cicada_p_1 + C # coord_cartesian(ylim = c(0, 5.25))
cicada_p_1 <- cicada_p_1 + TM4
cicada_p_1 <- cicada_p_1 + Plt #scale_colour_manual(values = PL(n_colors))
cicada_p_1 <- cicada_p_1 +  Xlab1 #xlab("Acoustic stimuli")
cicada_p_1 <- cicada_p_1 +  Ylab1 #ylab("Mean response score")
cicada_p_1 <- cicada_p_1 +  FW #facet_wrap(~ Species_full)
cicada_p_1 

#shorthand
cicada_p_1 <- ggplot(data = cicada, aes(x = Playback, y = Response, colour = Species_full))   + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cicada_p_1 
 
 #ggsave("cicadas_plot1.jpg")

#save with tilty text, save with 8 x 17 defaults
#save without x axis

```

cicada plot 2

```{r}

cicada_p_2 <- ggplot(data = cicada, aes(x = Species_full, y = Response, colour = Species_full))
cicada_p_2  <- cicada_p_2  + geom_point(position = position_jitter(width = 0.1)) #size = 5

cicada_p_2 <- cicada_p_2 + coord_cartesian(ylim = c(0, 5.25))
cicada_p_2 <- cicada_p_2 + TM2
cicada_p_2 <- cicada_p_2 + scale_colour_manual(values = PL(n_colors))
cicada_p_2 <- cicada_p_2 +  xlab("Acoustic stimuli")
cicada_p_2 <- cicada_p_2 +  ylab("Response score")
cicada_p_2 <- cicada_p_2 + facet_wrap(~ Playback, ncol =2) #ncol controls the number of columns, could easily be 2
cicada_p_2 

#shorthand
cicada_p_2  <-cicada_p_2 <- ggplot(data = cicada, aes(x = Species_full, y = Response, colour = Species_full)) +  GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
cicada_p_2
 
 #ggsave("cicadas_plot2.jpg", width = 7, height =7)
Z_smar = subset(cicada, cicada$Playback == "Z. smaragdina")

p_Z.smar<- p_Z.smar <- ggplot(data = Z_smar, aes(x = Species_full, y = Response, colour = "yellow4"))
p_Z.smar  <- p_Z.smar  + geom_point(position = position_jitter(width = 0.08), size = 3) #size = 5
p_Z.smar <- p_Z.smar + coord_cartesian(ylim = c(0, 5.25))
p_Z.smar <- p_Z.smar + TM2.5
p_Z.smar <- p_Z.smar + scale_colour_manual(values = "turquoise3")
p_Z.smar <- p_Z.smar +  xlab("Acoustic stimuli")
p_Z.smar <- p_Z.smar +  ylab("Response score")

p_Z.smar 
  
#  ggsave("p_Z.smar.jpg", width = 8,  height = 7)


Q_gigas = subset(cicada, cicada$Playback == "Q. gigas")

p_Q.gigas<- p_Q.gigas <- ggplot(data = Q_gigas, aes(x = Species_full, y = Response, colour = "yellow4"))
p_Q.gigas  <- p_Q.gigas  + geom_point(position = position_jitter(width = 0.08), size = 3) #size = 5
p_Q.gigas <- p_Q.gigas + coord_cartesian(ylim = c(0, 5.25))
p_Q.gigas <- p_Q.gigas + TM2.5
p_Q.gigas <- p_Q.gigas + scale_colour_manual(values = "yellow4")
p_Q.gigas <- p_Q.gigas +  xlab("Acoustic stimuli")
p_Q.gigas <- p_Q.gigas +  ylab("Response score")

p_Q.gigas 
  
#  ggsave("p_Q.gigas.jpg", width = 8,  height = 7)






```

## cicadas averages

cicada plot 1

```{r}
cicada_avg <- subset( Resp_avg, Resp_avg$Playback == "Q. gigas" | Resp_avg$Playback == "Z. smaragdina")

cicada_p_1_a <- ggplot(data = cicada_avg, aes(x = Playback, y = Resp_average, colour = Species_full))  + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cicada_p_1_a 

 
 #ggsave("cicadas_plot1_avg.jpg")



##cicada plot 2


cicada_p_2_a <- ggplot(data = cicada_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
cicada_p_2_a

 
 #ggsave("cicadas_plot2_avg.jpg", width = W2, height = H2)

```

## Crickets

cricket plot 1

```{r}
cricket <- subset( g_u, g_u$Playback == "Acla sp." | g_u$Playback == "Anaxipha sp." | g_u$Playback == "Aclodes sp.")

cricket_p_1 <- ggplot(data = cricket, aes(x = Playback, y = Response, colour = Species_full))  + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cricket_p_1 

 
 #ggsave("crickets_plot1.jpg")



```

cricket plot 2

```{r}

cricket_p_2 <- ggplot(data = cricket, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
cricket_p_2 

 
 #ggsave("crickets_plot2.jpg", width = W2, height = H2)

```

## crickets averages

cricket plot 1

```{r}
cricket_avg <- subset( Resp_avg, Resp_avg$Playback == "Acla sp." | Resp_avg$Playback == "Anaxipha sp." | Resp_avg$Playback == "Aclodes sp.")

cricket_p_1_a <- ggplot(data = cricket_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cricket_p_1_a 

 
 #ggsave("crickets_plot1_avg.jpg")



##cricket plot 2


cricket_p_2_a <- ggplot(data = cricket_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
cricket_p_2_a

 
 #ggsave("crickets_plot2_avg.jpg", width = W2, height = H2)

```

#INCIDENTAL SOUNDS incidental plot 1

```{r}
incidental <- subset( g_u, g_u$Playback == "Beetle flight" | g_u$Playback == "Frog hopping" | g_u$Playback == "Mouse rustles")

incidental_p_1 <- ggplot(data = incidental, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
incidental_p_1 

 
 #ggsave("incidentals_plot1.jpg")


```

incidental plot 2

```{r}

incidental_p_2 <- ggplot(data = incidental, aes(x = Species_full, y = Response, colour = Species_full)) +  GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
incidental_p_2 

 
 #ggsave("incidentals_plot2.jpg", width = W2, height = H2)

```

## incidentals averages

incidental plot 1

```{r}

incidental_avg <- subset( Resp_avg, Resp_avg$Playback == "Beetle flight" | Resp_avg$Playback == "Frog hopping" | Resp_avg$Playback == "Mouse rustles")

incidental_p_1_a <- ggplot(data = incidental_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
incidental_p_1_a 

 
 #ggsave("incidentals_plot1_avg.jpg")



##incidental plot 2


incidental_p_2_a <- ggplot(data = incidental_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
incidental_p_2_a

 
 #ggsave("incidentals_plot2_avg.jpg", width = W2, height = H2)

```

#White SOUNDS incidenteal plot 1

```{r}
White <- subset( g_u, g_u$Playback == "White noise")

White_p_1 <- ggplot(data = White, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
White_p_1 

 
 #ggsave("Whites_plot1.jpg")


```

White plot 2

```{r}

White_p_2 <- ggplot(data = White, aes(x = Species_full, y = Response, colour = Species_full)) +  GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
White_p_2 

 
 #ggsave("Whites_plot2.jpg", width = W2, height = H2)

```

## Whites averages

White plot 1

```{r}

White_avg <- subset( Resp_avg, Resp_avg$Playback == "White noise") 

White_p_1_a <- ggplot(data = White_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
White_p_1_a 

 
 #ggsave("Whites_plot1_avg.jpg")



##White plot 2


White_p_2_a <- ggplot(data = White_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
White_p_2_a

 
 #ggsave("Whites_plot2_avg.jpg", width = W2, height = H2)

```

\`

## geckos

gecko plot 1

```{r}
gecko <- subset( g_u, g_u$Playback == "H. frenatus" | g_u$Playback == "T. rapicauda")

gecko_p_1 <- ggplot(data = gecko, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
gecko_p_1 

 
 #ggsave("geckos_plot1.jpg")



```

gecko plot 2

```{r}

gecko_p_2 <- ggplot(data = gecko, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
gecko_p_2 

 
 #ggsave("geckos_plot2.jpg", width = W2, height = H2)

```

## geckos averages

gecko plot 1

```{r}
gecko_avg <- subset( Resp_avg, Resp_avg$Playback == "H. frenatus" | Resp_avg$Playback == "T. rapicauda")

gecko_p_1_a <- ggplot(data = gecko_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
gecko_p_1_a 

 
 #ggsave("geckos_plot1_avg.jpg")



##gecko plot 2


gecko_p_2_a <- ggplot(data = gecko_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
gecko_p_2_a

 
 #ggsave("geckos_plot2_avg.jpg", width = W2, height = H2)

```

## Frogs

frog plot 1

```{r}
frog <- subset( g_u, g_u$Playback == "H. fleishmanni" | g_u$Playback == "D. diastema" | g_u$Playback == "D. ebraccatus "| g_u$Playback == "P. pustulosus" | g_u$Playback =="S. sila")

frog_p_1 <- ggplot(data = frog, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
frog_p_1 

 
 #ggsave("frogs_plot1.jpg")

 
   Trac_frog_p <-    ggplot(data = subset(frog, frog$Species =="Trac_cirr"), aes(x = Playback, y = Response, colour = Playback))    + G + C  + TM3 + Plt+  Xlab1 +  Ylab1 +  FW 
   Trac_frog_p
   ggsave("Trac_frog_p.jpg")
frog_p_1 
 

```

frog plot 2

```{r}

frog_p_2 <- ggplot(data = frog, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
frog_p_2 

 
 #ggsave("frogs_plot2.jpg", width = W2, height = H2)

```

## frogs averages

frog plot 1

```{r}
frog_avg <- subset( Resp_avg, Resp_avg$Playback == "H. fleishmanni" | Resp_avg$Playback == "D. diastema" | Resp_avg$Playback == "D. ebraccatus "| Resp_avg$Playback == "P. pustulosus" | Resp_avg$Playback =="S. sila")

frog_p_1_a <- ggplot(data = frog_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
frog_p_1_a 

 
 #ggsave("frogs_plot1_avg.jpg")



##frog plot 2


frog_p_2_a <- ggplot(data = frog_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
frog_p_2_a

 
 #ggsave("frogs_plot2_avg.jpg", width = W2, height = H2)

```

## katydids

katydid plot 1

```{r}
katydid <- subset( g_u, g_u$Playback == "A. spatulata" | g_u$Playback == "C. wheeleri" | g_u$Playback == "D. gigliotosi"| g_u$Playback == "T. subfalcata" | g_u$Playback =="V. zederstedi")

katydid_p_1 <- ggplot(data = katydid, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM3 + Plt+  Xlab1 +  Ylab1 +  FW 
katydid_p_1

 
 #ggsave("katydids_plot1_axis.jpg")



```

katydid plot 2

```{r}

katydid_p_2 <- ggplot(data = katydid, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
katydid_p_2 

 
 #ggsave("katydids_plot2.jpg", width = W2, height = H2)

```

## katydids averages

katydid plot 1

```{r}
katydid_avg <- subset( Resp_avg, Resp_avg$Playback == "A. spatulata" | Resp_avg$Playback == "C. wheeleri" | Resp_avg$Playback == "D. gigliotosi"| Resp_avg$Playback == "T. subfalcata" | Resp_avg$Playback =="V. zederstedi")

katydid_p_1_a <- ggplot(data = katydid_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM3 + Plt+  Xlab1 +  Ylab1 +  FW 
katydid_p_1_a 

 
 #ggsave("katydids_plot1_avg_axis.jpg")



##katydid plot 2


katydid_p_2_a <- ggplot(data = katydid_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
katydid_p_2_a

 
 #ggsave("katydids_plot2_avg.jpg", width = W2, height = H2)

```

########################## 

########################## 


### Stats ###




## RUNNING TESTS TO SEE WHETHER DIFFERENT BATS RESPOND TO SOUNDS DIFFERENTLY

Should I do iterative selection with call type, to see how species
respond to different calltypes? Should I see if calltype and playback
should both be in the model? Does that make sense, if playback is
nested in call type? \## Call type

```{r}
# Does playback predict response? Yes
G_U_clmm_pl<- clmm(as.factor(Response) ~ Playback + (1| ID), data= g_u)
summary(G_U_clmm_pl) 

#with number as random effect (number has a bunch of weird values, at present though)
G_U_clmm_pl1<- clmm(as.factor(Response) ~ Playback + (1| ID)+ (1|Number), data= g_u)
summary(G_U_clmm_pl1) 

#write.csv2(G_U_clmm_pl1, "G_U_clmm_pl1.csv") #doesn't work, but would be good to export these. Maybe by date?

#rankedmodels_randomeffect<- rankModels(list( G_U_clmm_pl, G_U_clmm_pl1 ))
#^doesn't work yet, mod 11.30.20

# Does category predict response? YES
G_U_clmm_CT<- clmm(as.factor(Response) ~ Call_type + (1| ID), data= g_u)
summary(G_U_clmm_CT) 
em_CT <-emmeans(G_U_clmm_CT, "Call_type")
em_CT
plot(em_CT)
# ggsave("over_bat_response_call_type.jpg")
G_U_clmm<- clmm(as.factor(Response) ~ Species*Playback + (1| Number), data= g_u)
summary(G_U_clmm)
```

## Playback- AICC ranked model selection

-   Add number as random effect

```{r}

g1_01<- clmm(as.factor(Response) ~ Species * Playback + (1|ID), data= g_u, Hess=TRUE, nAGQ=10) #full model
g1_02<- clmm(as.factor(Response) ~ Species + Playback + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)
g1_03<- clmm(as.factor(Response) ~ Species + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)
g1_04<- clmm(as.factor(Response) ~ Playback + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)
g1_05<- clmm(as.factor(Response) ~ 1 + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)


rankModels(list(g1_01, g1_02, g1_03, g1_04, g1_05))
rankedmodels_g1<-rankModels(list(g1_01, g1_02, g1_03, g1_04, g1_05))
rankedmodels_g1

#add column with formulas? 
modelnames<- c("2- species + playback" , "1- species * playback", "3- species", "4- playback", "5- intercept only")
rankedmodels_g1 <- cbind(modelnames, rankedmodels_g1)

write.csv(rankedmodels_g1, file="ranked_models_speciesxplayback.csv")
#so additive model is better than model with interaction...

Anova_species_playback <- anova(g1_01, g1_02)
Anova_species_playback 

## So this analysis thinks that species predicts responses, and playback predicts responses, but different species don't respond differently to different playbacks (including all the species with more than 1 response). But the first model was just really hard to fit. May be that mostly bats responded to the sounds just as hthings to listen to, and since most of the bats didn't respond to sounds, then that was the dominant effect)
# no "main effect" with these categorical variables... so maybe "add 1" strategy? to look at each factor seperately?

# https://towardsdatascience.com/model-selection-101-using-r-c8437b5f9f99

# (maybe remove variables with less than 2?)
#1 pull out species with at least 1 land, and test them, to pull out species that we know are paying attention for food purposes. 

#could also do an analysis with the bats that are most likely to just be listening: AJS, discolor. try to parse what just listening looks like vs what hunting looks like. 

# also pull out a species and look at preferences

```



### TEST ACOUSTIC PREFERENCES: MULTICOLLINEARITY

```{r}
# Make models to test for Multicollinearity, choose variables that don't super covary
g_u$pulses_call <- as.numeric(g_u$pulses_call)
g_u$duty_cycle<- as.numeric(g_u$duty_cycle)
g_u$sum_pulse_duration_callgroup <- as.numeric(g_u$sum_pulse_duration_callgroup)

## pretty nuch every acoustic variable must be logged
hist(g_u$amplitude)
hist(log(g_u$amplitude))

#  removed variables+ log(pulses_call)
model <- glm(Response ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + amplitude , data= g_u)
summary(model)
alias(model)
vif(model) 

# with call types logged, these are not multicollinear @ > 5

```

```{r, eval = FALSE}
#Testing overall acoustic preferences for all bats (following a guide from Hannah ter Hofstede for model selection, but this is pretty rough)

#c_AP_1<- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
#summary(c_AP_1)
#6 predictor variables
#CAP_1 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)

#CAP_2 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) +  (1|ID) , data= g_u)

CAP_3 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= g_u)

#CAP_4 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   +  log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)

#CAP_5 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)

#CAP_6 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)  + log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)

#CAP_7 <- clmm(as.factor(Response) ~   log(peak_freq) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)

#CAP_8 <- clmm(as.factor(Response) ~   log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
#CAP_9<- clmm(as.factor(Response) ~   log(peak_freq)   + log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
#CAP_10 <- clmm(as.factor(Response) ~   log(peak_freq) + log(bandw)  + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
CAP_11 <- clmm(as.factor(Response) ~   log(peak_freq) + log(bandw)   + log(duty_cycle) +  amplitude + (1|ID) , data= g_u)
#CAP_12 <- clmm(as.factor(Response) ~   log(peak_freq) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + (1|ID) , data= g_u)

#CAP_13 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup)   + log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)

#CAP_14 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)    + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
CAP_15 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= g_u)
#CAP_16 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + (1|ID) , data= g_u)
CAP_17 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
CAP_18 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle)  + amplitude + (1|ID) , data= g_u)
#CAP_19 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle) + log(file_time_with_sound) +  (1|ID) , data= g_u)
CAP_20 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)  + amplitude + (1|ID) , data= g_u)
#CAP_21 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(file_time_with_sound)  + (1|ID) , data= g_u)
CAP_22 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + (1|ID) , data= g_u)
CAP_23 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)  + (1|ID) , data= g_u) #first 3
CAP_24 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle) +  (1|ID) , data= g_u)
#CAP_25 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +   log(file_time_with_sound) +  (1|ID) , data= g_u)
CAP_26 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  amplitude + (1|ID) , data= g_u)
CAP_27 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + log(duty_cycle)  + (1|ID) , data= g_u)
#CAP_28 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   +  log(file_time_with_sound) + (1|ID) , data= g_u)
CAP_29 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + amplitude + (1|ID) , data= g_u)
#CAP_30 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(duty_cycle) + log(file_time_with_sound) + (1|ID) , data= g_u)
CAP_30 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(duty_cycle) + amplitude + (1|ID) , data= g_u)
#CAP_31 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
CAP_32 <- clmm(as.factor(Response) ~  log(peak_freq) + log(bandw)   + log(duty_cycle) +  (1|ID) , data= g_u)
#CAP_33 <- clmm(as.factor(Response) ~ log(peak_freq) + log(bandw)   + log(file_time_with_sound) + (1|ID) , data= g_u)
CAP_34 <- clmm(as.factor(Response) ~  log(peak_freq) + log(bandw)   + amplitude + (1|ID) , data= g_u)
CAP_35 <- clmm(as.factor(Response) ~ log(bandw)   + log(duty_cycle) + log(file_time_with_sound) +  (1|ID) , data= g_u)
CAP_36 <- clmm(as.factor(Response) ~  log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= g_u)
CAP_37 <- clmm(as.factor(Response) ~  log(duty_cycle) + log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
CAP_38 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + (1|ID) , data= g_u)
CAP_39 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + (1|ID) , data= g_u)
CAP_40 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(duty_cycle)  + (1|ID) , data= g_u)
CAP_41 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(file_time_with_sound) +(1|ID) , data= g_u)
CAP_42 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + amplitude + (1|ID) , data= g_u)
CAP_43 <- clmm(as.factor(Response) ~ log(peak_freq) + log(bandw) + (1|ID) , data= g_u)
CAP_44 <- clmm(as.factor(Response) ~ log(peak_freq)  + log(duty_cycle) +  (1|ID) , data= g_u)
CAP_45 <- clmm(as.factor(Response) ~ log(peak_freq) + log(file_time_with_sound)  + (1|ID) , data= g_u)
CAP_46 <- clmm(as.factor(Response) ~ log(peak_freq) + amplitude + (1|ID) , data= g_u)
CAP_47 <- clmm(as.factor(Response) ~ log(bandw)  + log(duty_cycle)  + (1|ID) , data= g_u)
CAP_48 <- clmm(as.factor(Response) ~  log(bandw) + log(file_time_with_sound) + (1|ID) , data= g_u)
CAP_49 <- clmm(as.factor(Response) ~ log(bandw)  + amplitude + (1|ID) , data= g_u)
CAP_50 <- clmm(as.factor(Response) ~ log(duty_cycle) + log(file_time_with_sound)  + (1|ID) , data= g_u)
CAP_51 <- clmm(as.factor(Response) ~ log(duty_cycle) + amplitude + (1|ID) , data= g_u)
CAP_52 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + (1|ID) , data= g_u)
CAP_53 <- clmm(as.factor(Response) ~ log(peak_freq) + (1|ID) , data= g_u)
CAP_54 <- clmm(as.factor(Response) ~ log(bandw)  + (1|ID) , data= g_u)
CAP_55 <- clmm(as.factor(Response) ~  log(duty_cycle)+ (1|ID) , data= g_u)
CAP_56 <- clmm(as.factor(Response) ~  log(file_time_with_sound) + (1|ID) , data= g_u)
CAP_57 <- clmm(as.factor(Response) ~ amplitude + (1|ID) , data= g_u)


ALL_Tbl <- rankModels( list(CAP_1,
CAP_2	,
CAP_3	,
CAP_4	,
CAP_5	,
CAP_6	,
CAP_7	,
CAP_8	,
CAP_9	,
CAP_10	,
CAP_11	,
CAP_12	,
CAP_13	,
CAP_14	,
CAP_15	,
CAP_16	,
CAP_17	,
CAP_18	,
CAP_19	,
CAP_20	,
CAP_21	,
CAP_22	,
CAP_23	,
CAP_24	,
CAP_25	,
CAP_26	,
CAP_27	,
CAP_28	,
CAP_29	,
CAP_30	,
CAP_31	,
CAP_32	,
CAP_33	,
CAP_34	,
CAP_35	,
CAP_36	,
CAP_37	,
CAP_38	,
CAP_39	,
CAP_40	,
CAP_41	,
CAP_42	,
CAP_43	,
CAP_44	,
CAP_45	,
CAP_46	,
CAP_47	,
CAP_48	,
CAP_49	,
CAP_50	,
CAP_51	,
CAP_52	,
CAP_53	,
CAP_54	,
CAP_55	,
CAP_56	,
CAP_57))	
ALL_Tbl
## 

#There is a 71% chance that the full model is the best model, compared to 28.5% for the next best model. 

```

```{r, eval = FALSE}
#what about without file time with sound? 5 factors

CAP_1 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= g_u)


CAP_2 <- clmm(as.factor(Response) ~   log(peak_freq) + log(bandw)   + log(duty_cycle) +  amplitude + (1|ID) , data= g_u)

CAP_3 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= g_u)

CAP_4 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(file_time_with_sound) + amplitude + (1|ID) , data= g_u)
CAP_5 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle)  + amplitude + (1|ID) , data= g_u)
CAP_6 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)  + amplitude + (1|ID) , data= g_u)
CAP_7 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + (1|ID) , data= g_u)
CAP_8 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)  + (1|ID) , data= g_u) #first 3
CAP_9 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle) +  (1|ID) , data= g_u)
CAP_10 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  amplitude + (1|ID) , data= g_u)
CAP_11 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + log(duty_cycle)  + (1|ID) , data= g_u)
CAP_12 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + amplitude + (1|ID) , data= g_u)
CAP_13 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(duty_cycle) + amplitude + (1|ID) , data= g_u)

CAP_14 <- clmm(as.factor(Response) ~  log(peak_freq) + log(bandw)   + log(duty_cycle) +  (1|ID) , data= g_u)
CAP_15 <- clmm(as.factor(Response) ~  log(peak_freq) + log(bandw)   + amplitude + (1|ID) , data= g_u)
CAP_16 <- clmm(as.factor(Response) ~  log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= g_u)
CAP_17 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + (1|ID) , data= g_u)
CAP_18 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + (1|ID) , data= g_u)
CAP_19 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(duty_cycle)  + (1|ID) , data= g_u)
CAP_20 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + amplitude + (1|ID) , data= g_u)
CAP_21 <- clmm(as.factor(Response) ~ log(peak_freq) + log(bandw) + (1|ID) , data= g_u)
CAP_22 <- clmm(as.factor(Response) ~ log(peak_freq)  + log(duty_cycle) +  (1|ID) , data= g_u)
CAP_23 <- clmm(as.factor(Response) ~ log(peak_freq) + amplitude + (1|ID) , data= g_u)
CAP_24 <- clmm(as.factor(Response) ~ log(bandw)  + log(duty_cycle)  + (1|ID) , data= g_u)
CAP_25 <- clmm(as.factor(Response) ~ log(bandw)  + amplitude + (1|ID) , data= g_u)
CAP_26 <- clmm(as.factor(Response) ~ log(duty_cycle) + amplitude + (1|ID) , data= g_u)
CAP_27 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + (1|ID) , data= g_u)
CAP_28 <- clmm(as.factor(Response) ~ log(peak_freq) + (1|ID) , data= g_u)
CAP_29 <- clmm(as.factor(Response) ~ log(bandw)  + (1|ID) , data= g_u)
CAP_30 <- clmm(as.factor(Response) ~  log(duty_cycle)+ (1|ID) , data= g_u)
CAP_31 <- clmm(as.factor(Response) ~ amplitude + (1|ID) , data= g_u)


ALL_Tbl <- rankModels( list(CAP_1,
CAP_2	,
CAP_3	,
CAP_4	,
CAP_5	,
CAP_6	,
CAP_7	,
CAP_8	,
CAP_9	,
CAP_10	,
CAP_11	,
CAP_12	,
CAP_13	,
CAP_14	,
CAP_15	,
CAP_16	,
CAP_17	,
CAP_18	,
CAP_19	,
CAP_20	,
CAP_21	,
CAP_22	,
CAP_23	,
CAP_24	,
CAP_25	,
CAP_26	,
CAP_27	,
CAP_28	,
CAP_29	,
CAP_30	,
CAP_31))

ALL_Tbl
 anova(CAP_1, CAP_6)
#

## 


```

Likelihood ratio tests of cumulative link models:

      formula:                                                                                                                      

CAP_6 as.factor(Response) \~ log(sum_pulse_duration_callgroup) +
log(peak_freq) + log(bandw) + amplitude + (1 \| ID)\
CAP_1 as.factor(Response) \~ log(sum_pulse_duration_callgroup) +
log(peak_freq) + log(bandw) + log(duty_cycle) + amplitude + (1 \| ID)
link: threshold: CAP_6 logit flexible\
CAP_1 logit flexible

      no.par    AIC  logLik LR.stat df Pr(>Chisq)  

CAP_6 10 2831.5 -1405.7\
CAP_1 11 2827.6 -1402.8 5.8215 1 0.01583 \* --- Signif. codes: 0 '***'
0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

WHAT ABOUT LOPHOSTOMA?

```{r, eval = FALSE}

#LOPHOSTOMA BEST MODEL?
Loph_g_u<- subset(g_u, g_u$Species == "Loph_silv")
head(Loph_g_u)

model <- glm(Response ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) +  amplitude , data= Loph_g_u)
summary(model)
alias(model)
vif(model) 
#All below 5, proceed (though close to...)
LoS_1 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= Loph_g_u)


LoS_2 <- clmm(as.factor(Response) ~   log(peak_freq) + log(bandw)   + log(duty_cycle) +  amplitude + (1|ID) , data= Loph_g_u)

LoS_3 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= Loph_g_u)

LoS_4 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(file_time_with_sound) + amplitude + (1|ID) , data= Loph_g_u)
LoS_5 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle)  + amplitude + (1|ID) , data= Loph_g_u)
LoS_6 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)  + amplitude + (1|ID) , data= Loph_g_u)
LoS_7 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + (1|ID) , data= Loph_g_u)
LoS_8 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)  + (1|ID) , data= Loph_g_u) #first 3
LoS_9 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  log(duty_cycle) +  (1|ID) , data= Loph_g_u)
LoS_10 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) +  amplitude + (1|ID) , data= Loph_g_u)
LoS_11 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + log(duty_cycle)  + (1|ID) , data= Loph_g_u)
LoS_12 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + amplitude + (1|ID) , data= Loph_g_u)
LoS_13 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(duty_cycle) + amplitude + (1|ID) , data= Loph_g_u)

LoS_14 <- clmm(as.factor(Response) ~  log(peak_freq) + log(bandw)   + log(duty_cycle) +  (1|ID) , data= Loph_g_u)
LoS_15 <- clmm(as.factor(Response) ~  log(peak_freq) + log(bandw)   + amplitude + (1|ID) , data= Loph_g_u)
LoS_16 <- clmm(as.factor(Response) ~  log(bandw)   + log(duty_cycle) + amplitude + (1|ID) , data= Loph_g_u)
LoS_17 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + (1|ID) , data= Loph_g_u)
LoS_18 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + log(bandw)   + (1|ID) , data= Loph_g_u)
LoS_19 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) +  log(duty_cycle)  + (1|ID) , data= Loph_g_u)
LoS_20 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + amplitude + (1|ID) , data= Loph_g_u)
LoS_21 <- clmm(as.factor(Response) ~ log(peak_freq) + log(bandw) + (1|ID) , data= Loph_g_u)
LoS_22 <- clmm(as.factor(Response) ~ log(peak_freq)  + log(duty_cycle) +  (1|ID) , data= Loph_g_u)
LoS_23 <- clmm(as.factor(Response) ~ log(peak_freq) + amplitude + (1|ID) , data= Loph_g_u)
LoS_24 <- clmm(as.factor(Response) ~ log(bandw)  + log(duty_cycle)  + (1|ID) , data= Loph_g_u)
LoS_25 <- clmm(as.factor(Response) ~ log(bandw)  + amplitude + (1|ID) , data= Loph_g_u)
LoS_26 <- clmm(as.factor(Response) ~ log(duty_cycle) + amplitude + (1|ID) , data= Loph_g_u)
LoS_27 <- clmm(as.factor(Response) ~ log(sum_pulse_duration_callgroup) + (1|ID) , data= Loph_g_u)
LoS_28 <- clmm(as.factor(Response) ~ log(peak_freq) + (1|ID) , data= Loph_g_u)
LoS_29 <- clmm(as.factor(Response) ~ log(bandw)  + (1|ID) , data= Loph_g_u)
LoS_30 <- clmm(as.factor(Response) ~  log(duty_cycle)+ (1|ID) , data= Loph_g_u)
LoS_31 <- clmm(as.factor(Response) ~ amplitude + (1|ID) , data= Loph_g_u)


LoS_Tbl <- rankModels( list(LoS_1,
LoS_2	,
LoS_3	,
LoS_4	,
LoS_5	,
LoS_6	,
LoS_7	,
LoS_8	,
LoS_9	,
LoS_10	,
LoS_11	,
LoS_12	,
LoS_13	,
LoS_14	,
LoS_15	,
LoS_16	,
LoS_17	,
LoS_18	,
LoS_19	,
LoS_20	,
LoS_21	,
LoS_22	,
LoS_23	,
LoS_24	,
LoS_25	,
LoS_26	,
LoS_27	,
LoS_28	,
LoS_29	,
LoS_30	,
LoS_31))

LoS_Tbl
 anova(LoS_13, LoS_5)
 # not different from next best model
 
# LoS_1x <- clmm(as.factor(Response) ~ Call_type + log(sum_pulse_duration_callgroup) +  log(duty_cycle) + amplitude + (1|ID) , data= Loph_g_u, nAGQ = 10,  Hess=TRUE, control = clmm.control(maxIter = 200))
anova(LoS_1x,LoS_13)
#adding in category explains more variation than the acoustic variables

#amplitude , duty_cycle, pulse duration

###
P_LS_pf <- ggplot(data = Loph_g_u, aes(x = log(sum_pulse_duration_callgroup), y = Response, colour = Species_full))

P_LS_pf <- P_LS_pf+ geom_point(position = position_jitter(width = 0.5), size = 5)
P_LS_pf<- P_LS_pf+ coord_cartesian(ylim = c(0, 5.25))
#p_gu_LA <- p_gu_LA + scale_colour_manual(values = PL(n_colors))
P_LS_pf<- P_LS_pf + TM2
p_gu_LA <- p_gu_LA +  xlab("Acoustic stimuli")
p_gu_LA <- p_gu_LA +  ylab("Response score") 




summary(LoS_13)
em_ALoS<-emmeans(C_LoS_13, "Species")
em_ALoS
cld_ALos<- multcomp::cld(em_ALoS, letters=LETTERS)
cld_ALos


C_LoS_cat <- clmm(as.factor(Response) ~ Call_type + (1|ID) , Loph_g_u)
summary(C_LoS_cat)
emCat_LoS<- emmeans(C_LoS_cat, "Call_type" )
plot(emCat_LoS)
```

```{r, eval = FALSE}
as.numeric(g_u$duty_cycle)
colnames(g_u)
G_U_acoustic<- clmm(as.factor(Response) ~ sum_pulse_duration_callgroup + peak_freq + bandw + pulses_call  + duty_cycle + file_time_with_sound + amplitude + (1| Number), data= g_u)
summary(G_U_acoustic)

```

Do different bats have different responses to white noise?

```{r, eval = FALSE}
#White #

G_U_clmm_white<- clmm(as.factor(Response) ~ Species + (1| Number), data= g_u[  g_u$Playback==c("White noise"), ])

summary(G_U_clmm_white)
```

Do different bats have different responses to katydids?

BY BAT SPECIES

```{r, eval = FALSE}
#katydid #data

G_U_clmm_k_pl<- clmm(as.factor(Response) ~ Species + (1| Number), data= katydid)
summary(G_U_clmm_k_pl)

K_pl<-emmeans(G_U_clmm_k_pl, "Species")
K_pl
K_pl_cld<- multcomp::cld(K_pl, letters=LETTERS)
K_pl_cld
plot(K_pl_cld) #overall responses to katydids
#ggsave("emmeans_katydid_pl.jpg")

## BY KATYDID
katydid1 <- katydid
katydid1$Playback <- as.character(katydid1$Playback)

G_U_clmm_k_pl<- clmm(as.factor(Response) ~ as.character(Playback) + (1| Number), data= katydid1)
summary(G_U_clmm_k_pl)

K_pl<-emmeans(G_U_clmm_k_pl, "Playback")
K_pl
K_pl_cld<- multcomp::cld(K_pl, letters=LETTERS)
K_pl_cld
plot(K_pl_cld) #overall responses to katydids
#ggsave("emmeans_K_pl.jpg")

```

#####SOUND#######
