---
title: "GleanerU7.19.19"
author: "may"
date: "July 19, 2019"
output: html_document
---

Questions: 

Non-statistical: 
Which and how many species approach potential prey sounds?
  
Which potential prey sounds does each species  approach?

Does each species approach mating calls, incidental sounds, or both?

How many categories of calls does each species approach?

*****
Does each bat species have a similar level of response to the different prey sounds?: 
*****

Cumulative link mixed model:
Response variable: Bat interest score
Fixed effects: bat species, sound type
Random effects: bat ID (means I will have to have enough individuals per species)
Bat interest score ~ bat species * sound type (random=batID), family = logit
AICc to rank models (Committee suggests iterative model selection)
Main effect of call type = prey species face different levels of bat predation
Main effect of bat species = different bats have different levels of responsiveness to sounds
Interaction between ‘bat species’ and ‘call type’ = different bats are attracted to different calls
******
Do some bat species approach more categories of sounds than others? 
(generalists v specialists)
******
Kruskal–Wallis OR generalized linear mixed model (depending on data distribution)
Y = # categories approached
 x = bat species
Random = bat ID
#categories approached ~ bat species, random= bat ID, family=poisson

****
Which sound parameters are relevant to the preferences of each bat species? 
Cumulative link mixed models:
Response variable: Bat species interest score
Fixed effects: # pulses*, peak frequency, duty cycle, bandwidth, and duration
Random effects: bat ID
AICc to rank models
When highest-ranking models are nested: test for significant differences with likelihood ratio test
When no significant differences between models, select most parsimonious model with only significant variables

Which variables are included in the final model?

*May be hard to compare incidental noises with calls 
*********
How do the categories of sounds cluster? 
PCA


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libraries
```{r}
library(GmAMisc) 
library(readxl)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(RColorBrewer)
library(plotly)
library(car)
library(ordinal) 
library(emmeans)
library(multcompView)
```

```{r}
gleaner_universe_r_7_19_19 <- read_excel("~/Dropbox/GLEANER UNIVERSE STUDY/data sheets/gleaner_universe_r_7.19.19.xlsx")
g_u <- gleaner_universe_r_7_19_19

Call_analysis_avgs_R <- read_excel("~/Dropbox/GLEANER UNIVERSE STUDY/data sheets/Call_analysis_avgs_R.xlsx", 
+     col_types = c("text", "numeric", "numeric", 
+         "numeric", "numeric", "numeric", 
+         "numeric", "numeric", "text", "text", 
+         "text", "text", "text", "text", "numeric", 
+         "text"))

```

Palettes
```{r}
#theme: 
TM <- theme_calc(base_size = 25) + theme(axis.text.x = element_text(angle = 45, hjust=1), plot.background =element_blank(), legend.title = element_blank()) #tilted x-axis labels and title, no legend title

TM2<-theme_calc(base_size = 25) + theme(axis.text.x = element_text(angle = 45, hjust=1), axis.title.x=element_blank()) #tilted x-axis labels, no x title

TM4<-theme_calc(base_size = 25) + theme(axis.text.x = element_text(angle = 45, hjust=1), axis.title.x=element_blank(), legend.position="none") #tilted x-axis labels, no x title, no legend


TM1 <- theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), legend.title = element_blank(), plot.background =element_blank() ) #blank axes, blank legend title

TM3 <-  theme_calc() +theme(axis.title.x=element_blank(), axis.text.x = element_text(angle = 75, hjust=1), legend.position = "none") #tilted x-axis labels and title, for no size control, remoe base_size argument #for diagonal text, put angle = 45

TM4 <-  theme_calc() +theme(axis.title.x=element_blank(), axis.text.x=element_blank(), legend.position = "none") # no size control, no x axis labels

PL <-  "Spectral"
PL <- colorRampPalette(brewer.pal(n_colors, "Set3"))
PL = colorRampPalette(brewer.pal(11, "Spectral"))

#palette with a lot of colors
c25 <- c("dodgerblue2","#E31A1C", # red
                "green4",
                "#6A3D9A", # purple
                "#FF7F00", # orange
                "black","gold1",
                "skyblue2","#FB9A99", # lt pink
                "palegreen2",
                "#CAB2D6", # lt purple
                "#FDBF6F", # lt orange
                "gray70", "khaki2",
                "maroon","orchid1","deeppink1","blue1","steelblue4",
                "darkturquoise","green1","yellow4","yellow3",
                "darkorange4","brown")
pie(rep(1,25), col=c25)

n_colors<- length(unique(g_u$Species_full))
#this is the number of species in the plot/ dataset at any given time, can be used to change the palette

#+ theme(axis.text.x = element_text(angle = 45, hjust=1, size = 14), legend.position = "none") #format x-axis, and remove side legend #hjust 1 aligns labels
```


```{r}
unique(g_u$Species)
unique(g_u$Species_full)
unique(g_u$Playback)
class(g_u$Playback)
unique(g_u$Response)
class(g_u$Response)

## remove moth sounds for now

g_u <- subset(g_u, g_u$Playback!="Moth sounds") 
g_u <- subset(g_u, g_u$Playback!="NA") 

## Just for now remove Micronycteris schmidtorum, glyphonycteris
g_u <- subset(g_u, g_u$Species!="Micr_schm" & g_u$Species!="Glyp_davi") 


g_u$Playback<- factor(g_u$Playback, levels = c( "Acla sp."       ,     "Aclodes sp."   ,  "Anaxipha sp.", "A. spatulata" , "T. subfalcata", "V. zederstedi"  ,  "C. wheeleri" ,  "D. gigliotosi"  , "Q. gigas" ,  "Z. smaragdina"   ,  
        "D. diastema" , "H. fleishmanni", "D. ebraccatus" ,  "S. sila"     ,      "P. pustulosus" ,  "H. frenatus" , "T. rapicauda"  , 
    "Beetle flight",  "Frog hopping"  , "Mouse rustles", "White noise"), ordered = TRUE )
```


Code categories
```{r}
#Recode a variable with the cetegories

g_u<- g_u %>% mutate(Call_type = if_else(Playback %in% c("A. spatulata","C. wheeleri","D. gigliotosi" ,"T. subfalcata","V. zederstedi"), "Katydid", 
      if_else(Playback %in% c( "Acla sp.","Aclodes sp.",  "Anaxipha sp."), "Cricket", 
      if_else(Playback %in% c("D. diastema", "D. ebraccatus", "D. ebraccatus",  "H. fleishmanni", "P. pustulosus" ,"S. sila"), "Frog", 
      if_else(Playback %in% c("Q. gigas", "Z. smaragdina"), "Cicada", 
      if_else(Playback %in% c( "H. frenatus","T. rapicauda" ), "Gecko", 
      if_else(Playback %in% c("Beetle flight", "Frog hopping" , "Mouse rustles", "Moth sounds" ),"Movement cue", 
      if_else(Playback %in% c("White noise"), "White noise","Other"
      
      ))))))))



#order factor
g_u$Call_type<- factor(g_u$Call_type, levels = c( "Cricket" , "Katydid", "Frog"  ,"Gecko",   "Cicada" ,  "Movement cue",    "White noise" ), ordered = TRUE )

```


Recode response with 0, 4, 5,
```{r}
#Recode a variable with 0, 4, 5 

g_u<- g_u %>% mutate(Response_ApproachLand = if_else(Response %in% c("0","1","2" ,"3"), "0", if_else(Playback %in% c("4"), "4", if_else(Response %in%c("5"),"5", "other"))))

g_u<- g_u %>% mutate(Response_ApproachLand = case_when(
      Response == 0 ~ 0, 
      Response == 1 ~ 0,
      Response == 2 ~ 0,
      Response == 3 ~ 0,
      Response == 4 ~ 4, 
      Response == 5 ~ 5))

    

```

```{r}
#####
# adding in amplitude
#####
g_u<- g_u %>% mutate(amplitude = case_when(
      Call_type == "Katydid" ~ 86.8, 
      Call_type == "Frog" ~ 75,
      Call_type == "Gecko" ~ 76.07,
      Call_type == "Cricket" ~ 70.22,
      Call_type == "Cicada" ~ 83.07,
      Playback == "Beetle flight" ~ 41.52,
      Playback == "Frog hopping"~ 39.52,
      Playback == "Mouse rustles" ~ 37.66))

```

##Which and how many species approach potential prey sounds?##
##Which land?##
```{r}
#Pulling out Species that land
land_sp <- g_u %>% filter(Response == 5)
unique(land_sp$Species)
unique(land_sp$Playback)

nrow(land_sp)
l_sp<- cbind(land_sp$Species_full, land_sp$Playback)
View(l_sp)
 #A. spatulata  Beetle flight C. wheeleri   D. gigliotosi P. pustulosus
#Q. gigas      S. sila       T. subfalcata V. zederstedi
 
## "Loph_bras" "Loph_silv" "Trac_cirr" "Micr_micr" "Micr_hirs"

# THERE ARE 5 species HUNTING using sounds, for sure, hunting 7 things
```

## Which land or approach? 
```{r}
#Species that land or approach
approach_land_sp <- g_u %>% filter(Response == 5 | Response == 4) 
nrow(approach_land_sp )
unique(approach_land_sp$Species)
unique(approach_land_sp$Playback)
length(approach_land_sp$Playback == "A. spatulata")
# THERE ARE 10 species that maaybe use sounds to hunt, at least sometimes
#[1] "Loph_bras" "Loph_silv" "Gard_cren" "Trac_cirr" "Micr_hirs" "Micr_micr" "Phyl_hast"

nrow(approach_land_sp)
View(approach_land_sp)
unique(approach_land_sp$Playback)

# IS the frequency of approach to different treatments different than random? 

table_app_land<- table(approach_land_sp$Playback)
table_app_land

chisq.test(table_app_land)
#IDK if this is appropriate, but its not different at alpha .05. p = 0.09


    ```
 
 plot 
 
```{r}
PLOTS LAND OR APPROACH ONLY 

n_colors_LA<- length(unique(land_sp$Species_full))

p_gu_LA <- ggplot(data = land_sp, aes(x = Playback, y = Response, colour = Species_full))

p_gu_LA <- p_gu_LA + geom_point(position = position_jitter(width = 0.5), size = 5)
p_gu_LA <- p_gu_LA + coord_cartesian(ylim = c(0, 5.25))
#p_gu_LA <- p_gu_LA + scale_colour_manual(values = PL(n_colors))
p_gu_LA <- p_gu_LA + TM2
p_gu_LA <- p_gu_LA +  xlab("Acoustic stimuli")
p_gu_LA <- p_gu_LA +  ylab("Response score") 

p_gu_LA


#ggsave("p_lands_species.jpg", width = 19, height = 8)
#ggsave("p_lands_approaches_species.jpg", width = 19, height = 8)

```
 
```
     
 ## Do bats respond more to some categories compared to others? 
```{r}
# bat response ~ category ( number )
unique(g_u$Call_type)

clmm_call_type<- clmm(as.factor(Response) ~ Call_type + (1| Number), data= g_u)
summary(clmm_call_type)

em_call_type <-emmeans(clmm_call_type, "Call_type")
em_call_type
cld_call_type<- cld(em_call_type, letters=LETTERS)
cld_call_type
pwpp(em_call_type) 

plot(em_call_type)
class(em_call_type)


```
 
 ## Do bats approach or land on some categories more than others?
 
```{r}
# bat response ~ category ( number )

clm_AppLand_call_type<- clm(as.factor(Response_ApproachLand) ~ Call_type, data= g_u)

summary(clm_AppLand_call_type)

em_AppLand_call_type <-emmeans(clm_AppLand_call_type, "Call_type")
em_AppLand_call_type
cld_AppLand_call_type<- cld(em_AppLand_call_type, letters=LETTERS)
cld_AppLand_call_type
pwpp(em_AppLand_call_type) 

plot(em_AppLand_call_type)
class(em_AppLand_call_type)

```
     
 Response bat species average responses to different groups:((cant really do averages on ordinal scales, but works for visualization))
```{r}
Resp_avg<-g_u %>% group_by(Species_full, Playback ) %>%
      summarise(Resp_average = mean(Response, na.rm=TRUE))
Resp_avg
```




```{r}
g_u_p <- ggplot(data = g_u, aes(x = Playback, y = Response, colour = Species_full))

g_u_p <- g_u_p + geom_point(position = position_jitter(width = 0.1), size = 5)
g_u_p <- g_u_p + coord_cartesian(ylim = c(0, 5.25))
g_u_p <- g_u_p + scale_colour_manual(values = PL(n_colors))
g_u_p <- g_u_p + TM2
g_u_p <- g_u_p +  xlab("Acoustic stimuli")
g_u_p <- g_u_p +  ylab("Response score") 

g_u_p


#ggsave("gleaner_universe_fulltemp.jpg", width = 19, height = 8)

```

```{r}
g_u_pl <- ggplot(data = g_u, aes(x = Playback, y = Response, colour = Species_full))

g_u_pl <- g_u_pl + geom_point(position = position_jitter(width = 0.05), size = 5)
g_u_pl <- g_u_pl + coord_cartesian(ylim = c(0, 5.25))
g_u_pl <- g_u_pl + scale_colour_manual(values = PL(n_colors))
g_u_pl <- g_u_pl + TM3 #can take out x legend line if I want, TM3 or TM4
g_u_pl <- g_u_pl +  xlab("Acoustic stimuli")
g_u_pl <- g_u_pl +  ylab("Response score") + facet_wrap(~ Species_full) #this makes a nice facet

g_u_pl
#ggsave("faceted_responses_Full_X.jpg", width = 12)

```



##########################
##########################
AVERAGES

```{r}
Resp_avg

g_u_p_avg <- ggplot(data = Resp_avg, aes(x = Playback, y = Resp_average, colour = Species_full))
g_u_p_avg  <- g_u_p_avg  + geom_point(size = 8)
#g_u_p_avg  <- g_u_p_avg  + geom_point(position = position_jitter(width = 0.1))
g_u_p <- g_u_p + coord_cartesian(ylim = c(0, 5.25))
g_u_p_avg <- g_u_p_avg + TM
g_u_p_avg <- g_u_p_avg + scale_colour_manual(values = PL(n_colors))
g_u_p_avg <- g_u_p_avg +  xlab("Acoustic stimuli")
g_u_p_avg <- g_u_p_avg +  ylab("Mean response score")
g_u_p_avg 

 #
 #ggsave("gleaner_universe_avgtemp.jpg",  height = 8 ,width = 19) 

#save with tilty text, save with 8 x 17 defaults
#save without x axis
```




No axes graph 1
```{r}

g_u_p_nax <- g_u_p + TM1

 #ggsave("gleaner_universe_full_NAX.jpg", width = 17, height = 8)



```

No axes graph 2
```{r}

g_u_p_avg_NAX  <- g_u_p_avg + TM1
g_u_p_avg_NAX

 #ggsave("gleaner_universe_avg_NAX.jpg", width = 17, height = 8)

#Saving 17 x 3.91 in image
```


##faceted

```{r}
head(Resp_avg)

g_u_p_avg_f <- ggplot(data = Resp_avg, aes(x = Playback, y = Resp_average, colour = Species_full))
g_u_p_avg_f  <- g_u_p_avg_f  + geom_point(size = 5)
#g_u_p_avg_f  <- g_u_p_avg_f  + geom_point(position = position_jitter(width = 0.1))
g_u_p <- g_u_p + coord_cartesian(ylim = c(0, 5.25))
g_u_p_avg_f <- g_u_p_avg_f + TM4
g_u_p_avg_f <- g_u_p_avg_f + scale_colour_manual(values = PL(n_colors))
g_u_p_avg_f <- g_u_p_avg_f +  xlab("Acoustic stimuli")
g_u_p_avg_f <- g_u_p_avg_f +  ylab("Mean response score")
g_u_p_avg_f  <- g_u_p_avg_f + facet_wrap(~ Species_full)
g_u_p_avg_f
 #
 #ggsave("gleaner_universe_avg_facet_noX.jpg", width = 11) # height = 8 ,width = 17) 

#save with tilty text, save with 8 x 17 defaults
#save without x axis
```





###########################
###########################
##SUBSETS##

```{r}
  #### settings for plot type 3####
  G3<- geom_point(position = position_jitter(width = 0.1), size = 5)
  C3 <- coord_cartesian(ylim = c(0, 5.25))
  Plt2<-scale_colour_manual(values = PL(n_colors))
  Xlab2 <-  xlab("Acoustic stimuli")
  Ylab2 <-  ylab("Response score")
  Ylab3 <-  ylab(" Average response score")
  H2 <- 5  #height for plot output default
  W2<- 13 # height default
  
  # "#9E0142" "#CB334C" "#E95D47" "#F88D51" "#FDBE6E" "#FEE593" "#FFFFBF" "#EAF69E" "#BEE5A0" "#88CFA4" "#54AEAC" "#397EB8" "#5E4FA2"
  
   #Colors for graphs
cAJ<- scale_colour_manual(values = c("#9E0142")) #"#9E0142"
cGC<- scale_colour_manual(values = c("#CB334C"))
cLaB <- scale_colour_manual(values = c("#E95D47"))
cLA <- scale_colour_manual(values = c("#F88D51"))
cLoB <- scale_colour_manual(values = c("#FDBE6E"))
 cLS <- scale_colour_manual(values = c("#FEE593")) 
 cMH <- scale_colour_manual(values = c("#FFFFBF"))
 cMM <- scale_colour_manual(values = c("#EAF69E" ))
 cPH <- scale_colour_manual(values = c("#BEE5A0" ))
 cTS <-scale_colour_manual(values = c("#88CFA4" ))
 cTC <- scale_colour_manual(values = c("#54AEAC"))
 cTN <-scale_colour_manual(values = c( "#397EB8"))
 # "#5E4FA2"
 
 W3<- 19 #width
 H3<- 8  #height
```

The quick and dirty way to make color palette names
 [1] Art jam "#9E0142" "#CB334C" "#E95D47" "#F88D51" "#FDBE6E"
 [6] "#FEE593" "#FFFFBF" "#EAF69E" "#BEE5A0" "#88CFA4"
[11] "#54AEAC" "#397EB8" "#5E4FA2"

Trac Cirr PLOT with axes. use TM4 FOR NO AXES
```{r}
g_u_p_TC <- ggplot(data = g_u[g_u$Species =="Trac_cirr",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_TC <- g_u_p_TC + G3 +C3 + TM4 + Xlab2 + Ylab2  +cTC
g_u_p_TC

#ggsave("gleaner_universe_TC.jpg", width = W3, height = H3)

#and TC's with AVERAGES


g_u_p_TC_a <- ggplot(data = Resp_avg[Resp_avg$Species_full =="Trachops cirrhosus",], aes(x = Playback, y = Resp_average, colour = Species_full))

g_u_p_TC_a <- g_u_p_TC_a + G3 +C3 + TM4 + Xlab2 + Ylab2  +cTC
g_u_p_TC_a

#ggsave("gleaner_universe_TC_avg.jpg",  width = W3, height = H3)

```
AJ PLOT with axes. use TM4 FOR NO AXES
```{r}
g_u_p_AJ <- ggplot(data = g_u[g_u$Species =="Arti_jama",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_AJ <- g_u_p_AJ + G3 +C3 + TM4 + Xlab2 + Ylab2  +cAJ
g_u_p_AJ

#ggsave("gleaner_universe_AJ.jpg", width = W3, height = H3)

#and AJ's with AVERAGES


g_u_p_AJ_a <- ggplot(data = Resp_avg[Resp_avg$Species_full =="Artibeus jamaicensis",], aes(x = Playback, y = Resp_average, colour = Species_full))

g_u_p_AJ_a <- g_u_p_AJ_a + G3 +C3 + TM4 + Xlab2 + Ylab2  +cAJ
g_u_p_AJ_a

#ggsave("gleaner_universe_AJ_avg.jpg", width = W3, height = H3)

```

AJ ALL GRAPH
```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT


g_u_p_AJ <- ggplot(data = g_u[g_u$Species =="Arti_jama",], aes(x = Playback, y = Response, colour = Species_full))
g_u_p_AJ <- g_u_p_AJ + G3 +  C3 + TM4 + Xlab2 + Ylab2  +cAJ + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Artibeus jamaicensis",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4) #parameters for the averages
     
g_u_p_AJ

#ggsave("gleaner_universe_AJ_a.jpg", width = W3, height = H3)

```
```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT




g_u_p_TC <- ggplot(data = g_u[g_u$Species =="Trac_cirr",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_TC <- g_u_p_TC + G3 +C3 + TM4 + Xlab2 + Ylab2  +cTC + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Trachops cirrhosus",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_TC

#ggsave("gleaner_universe_TC_a.jpg", width = W3, height = H3)


```
```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT


g_u_p_LS <- ggplot(data = g_u[g_u$Species =="Loph_silv",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_LS <- g_u_p_LS + G3 +C3 + TM4 + Xlab2 + Ylab2  +cLS + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lophostoma silvicolum",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_LS

##ggsave("gleaner_universe_LS_a.jpg", width = W3, height = H3)


```

LOPH BRASILIENSE
```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT


g_u_p_LoB <- ggplot(data = g_u[g_u$Species =="Loph_bras",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_LoB <- g_u_p_LoB + G3 +C3 + TM4 + Xlab2 + Ylab2  +cLoB + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lophostoma brasiliense",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_LoB

#ggsave("gleaner_universe_LoB_a.jpg", width = W3, height = H3)


```

PHYLLOSTOMUS HASTATUS
```{r}

g_u_p_PH <- ggplot(data = g_u[g_u$Species =="Phyl_hast",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_PH <- g_u_p_PH + G3 +C3 + TM4 + Xlab2 + Ylab2  +cPH + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Phyllostomus hastatus",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_PH

#ggsave("gleaner_universe_PH_a.jpg", width = W3, height = H3)

```

Lampronycteris brachiotis
```{r}

g_u_p_LaB <- ggplot(data = g_u[g_u$Species =="Lamp_brach",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_LaB <- g_u_p_LaB + G3 +C3 + TM4 + Xlab2 + Ylab2  +cLaB + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Lampronycteris brachiotis",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_LaB

#ggsave("gleaner_universe_LaB_a.jpg", width = W3, height = H3)


```

```{r}
##EXPERIMENTS: ADDING MEANS TO SAME PLOT




g_u_p_GC <- ggplot(data = g_u[g_u$Species =="Gard_cren",], aes(x = Playback, y = Response, colour = Species_full))

g_u_p_GC <- g_u_p_GC + G3 +C3 + TM4 + Xlab2 + Ylab2  +cGC + #all parameters for general data
      
      geom_point(data =Resp_avg[Resp_avg$Species_full =="Gardnerycteris crenulatum",], mapping=aes(x = Playback, y = Resp_average), color = "black", shape=17, size = 4 ) #parameters for the averages
     
g_u_p_GC

#ggsave("gleaner_universe_GC_a.jpg", width = W3, height = H3)


```

## generalizable p1 and p2 things
```{r}

###settings for plot type 1###
  G1<- geom_point(size = 5) 
  G <- geom_point( size = 5, position = position_jitter(width = 0.1))
  C <- coord_cartesian(ylim =c(0, 5.25)) 
  Plt<-scale_colour_manual(values = PL(n_colors))
  Xlab1 <-  xlab("Acoustic stimuli")
  Ylab1 <-  ylab("Response score")
  FW <- facet_wrap(~ Species_full)
  
  #### plot 2####
  G2 <- geom_point()
  GG2 <- geom_point(position = position_jitter(width = 0.1), size = 3)
  C2 <- coord_cartesian(ylim = c(0, 5.25))
  Plt2<-scale_colour_manual(values = PL(n_colors))
  Xlab2 <-  xlab("Acoustic stimuli")
  Ylab2 <-  ylab("Response score")
  FW2<- facet_wrap(~ Playback) #ncol controls the number of columns, could easily be 2
  H2 <- 5  #height for plot output default
  W2<- 13 # height default
  
```

## Cicadas

cicada plot 1
```{r}
cicada <- subset( g_u, g_u$Playback == "Q. gigas" | g_u$Playback == "Z. smaragdina")

cicada_p_1 <- ggplot(data = cicada, aes(x = Playback, y = Response, colour = Species_full))
#cicada_p_1  <- cicada_p_1    #geom_point(size = 5) 
cicada_p_1  <- cicada_p_1  + G   #geom_point(position = position_jitter(width = 0.1))
cicada_p_1 <- cicada_p_1 + C # coord_cartesian(ylim = c(0, 5.25))
cicada_p_1 <- cicada_p_1 + TM4
cicada_p_1 <- cicada_p_1 + Plt #scale_colour_manual(values = PL(n_colors))
cicada_p_1 <- cicada_p_1 +  Xlab1 #xlab("Acoustic stimuli")
cicada_p_1 <- cicada_p_1 +  Ylab1 #ylab("Mean response score")
cicada_p_1 <- cicada_p_1 +  FW #facet_wrap(~ Species_full)
cicada_p_1 

#shorthand
cicada_p_1 <- ggplot(data = cicada, aes(x = Playback, y = Response, colour = Species_full))   + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cicada_p_1 
 
 #ggsave("cicadas_plot1.jpg")

#save with tilty text, save with 8 x 17 defaults
#save without x axis

```
cicada plot 2
```{r}

cicada_p_2 <- ggplot(data = cicada, aes(x = Species_full, y = Response, colour = Species_full))
cicada_p_2  <- cicada_p_2  + geom_point() #size = 5
cicada_p_2  <- cicada_p_2  + geom_point(position = position_jitter(width = 0.1))
cicada_p_2 <- cicada_p_2 + coord_cartesian(ylim = c(0, 5.25))
cicada_p_2 <- cicada_p_2 + TM3
cicada_p_2 <- cicada_p_2 + scale_colour_manual(values = PL(n_colors))
cicada_p_2 <- cicada_p_2 +  xlab("Acoustic stimuli")
cicada_p_2 <- cicada_p_2 +  ylab("Response score")
cicada_p_2 <- cicada_p_2 + facet_wrap(~ Playback, ncol =1) #ncol controls the number of columns, could easily be 2
cicada_p_2 

#shorthand
cicada_p_2  <-cicada_p_2 <- ggplot(data = cicada, aes(x = Species_full, y = Response, colour = Species_full)) +  GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
cicada_p_2
 
 #ggsave("cicadas_plot2.jpg", width = 7, height =7)

```
## cicadas averages
cicada plot 1
```{r}
cicada_avg <- subset( Resp_avg, Resp_avg$Playback == "Q. gigas" | Resp_avg$Playback == "Z. smaragdina")

cicada_p_1_a <- ggplot(data = cicada_avg, aes(x = Playback, y = Resp_average, colour = Species_full))  + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cicada_p_1_a 

 
 #ggsave("cicadas_plot1_avg.jpg")



##cicada plot 2


cicada_p_2_a <- ggplot(data = cicada_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
cicada_p_2_a

 
 #ggsave("cicadas_plot2_avg.jpg", width = W2, height = H2)

```

## Crickets
cricket plot 1
```{r}
cricket <- subset( g_u, g_u$Playback == "Acla sp." | g_u$Playback == "Anaxipha sp." | g_u$Playback == "Aclodes sp.")

cricket_p_1 <- ggplot(data = cricket, aes(x = Playback, y = Response, colour = Species_full))  + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cricket_p_1 

 
 #ggsave("crickets_plot1.jpg")



```
cricket plot 2
```{r}

cricket_p_2 <- ggplot(data = cricket, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
cricket_p_2 

 
 #ggsave("crickets_plot2.jpg", width = W2, height = H2)

```
## crickets averages
cricket plot 1
```{r}
cricket_avg <- subset( Resp_avg, Resp_avg$Playback == "Acla sp." | Resp_avg$Playback == "Anaxipha sp." | Resp_avg$Playback == "Aclodes sp.")

cricket_p_1_a <- ggplot(data = cricket_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
cricket_p_1_a 

 
 #ggsave("crickets_plot1_avg.jpg")



##cricket plot 2


cricket_p_2_a <- ggplot(data = cricket_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
cricket_p_2_a

 
 #ggsave("crickets_plot2_avg.jpg", width = W2, height = H2)

```

#INCIDENTAL SOUNDS
incidenteal plot 1
```{r}
incidental <- subset( g_u, g_u$Playback == "Beetle flight" | g_u$Playback == "Frog hopping" | g_u$Playback == "Mouse rustles")

incidental_p_1 <- ggplot(data = incidental, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
incidental_p_1 

 
 #ggsave("incidentals_plot1.jpg")


```
incidental plot 2
```{r}

incidental_p_2 <- ggplot(data = incidental, aes(x = Species_full, y = Response, colour = Species_full)) +  GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
incidental_p_2 

 
 #ggsave("incidentals_plot2.jpg", width = W2, height = H2)

```
## incidentals averages
incidental plot 1
```{r}

incidental_avg <- subset( Resp_avg, Resp_avg$Playback == "Beetle flight" | Resp_avg$Playback == "Frog hopping" | Resp_avg$Playback == "Mouse rustles")

incidental_p_1_a <- ggplot(data = incidental_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
incidental_p_1_a 

 
 #ggsave("incidentals_plot1_avg.jpg")



##incidental plot 2


incidental_p_2_a <- ggplot(data = incidental_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
incidental_p_2_a

 
 #ggsave("incidentals_plot2_avg.jpg", width = W2, height = H2)

```


#White SOUNDS
incidenteal plot 1
```{r}
White <- subset( g_u, g_u$Playback == "White noise")

White_p_1 <- ggplot(data = White, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
White_p_1 

 
 #ggsave("Whites_plot1.jpg")


```
White plot 2
```{r}

White_p_2 <- ggplot(data = White, aes(x = Species_full, y = Response, colour = Species_full)) +  GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
White_p_2 

 
 #ggsave("Whites_plot2.jpg", width = W2, height = H2)

```
## Whites averages
White plot 1
```{r}

White_avg <- subset( Resp_avg, Resp_avg$Playback == "White noise") 

White_p_1_a <- ggplot(data = White_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
White_p_1_a 

 
 #ggsave("Whites_plot1_avg.jpg")



##White plot 2


White_p_2_a <- ggplot(data = White_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
White_p_2_a

 
 #ggsave("Whites_plot2_avg.jpg", width = W2, height = H2)

```




`

## geckos
gecko plot 1
```{r}
gecko <- subset( g_u, g_u$Playback == "H. frenatus" | g_u$Playback == "T. rapicauda")

gecko_p_1 <- ggplot(data = gecko, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
gecko_p_1 

 
 #ggsave("geckos_plot1.jpg")



```
gecko plot 2
```{r}

gecko_p_2 <- ggplot(data = gecko, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
gecko_p_2 

 
 #ggsave("geckos_plot2.jpg", width = W2, height = H2)

```

## geckos averages
gecko plot 1
```{r}
gecko_avg <- subset( Resp_avg, Resp_avg$Playback == "H. frenatus" | Resp_avg$Playback == "T. rapicauda")

gecko_p_1_a <- ggplot(data = gecko_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
gecko_p_1_a 

 
 #ggsave("geckos_plot1_avg.jpg")



##gecko plot 2


gecko_p_2_a <- ggplot(data = gecko_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
gecko_p_2_a

 
 #ggsave("geckos_plot2_avg.jpg", width = W2, height = H2)

```



## Frogs
frog plot 1
```{r}
frog <- subset( g_u, g_u$Playback == "H. fleishmanni" | g_u$Playback == "D. diastema" | g_u$Playback == "D. ebraccatus "| g_u$Playback == "P. pustulosus" | g_u$Playback =="S. sila")

frog_p_1 <- ggplot(data = frog, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
frog_p_1 

 
 #ggsave("frogs_plot1.jpg")

 
   Trac_frog_p <-    ggplot(data = subset(frog, frog$Species =="Trac_cirr"), aes(x = Playback, y = Response, colour = Playback))    + G + C  + TM3 + Plt+  Xlab1 +  Ylab1 +  FW 
   Trac_frog_p
   ggsave("Trac_frog_p.jpg")
frog_p_1 
 

```
frog plot 2
```{r}

frog_p_2 <- ggplot(data = frog, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
frog_p_2 

 
 #ggsave("frogs_plot2.jpg", width = W2, height = H2)

```
## frogs averages
frog plot 1
```{r}
frog_avg <- subset( Resp_avg, Resp_avg$Playback == "H. fleishmanni" | Resp_avg$Playback == "D. diastema" | Resp_avg$Playback == "D. ebraccatus "| Resp_avg$Playback == "P. pustulosus" | Resp_avg$Playback =="S. sila")

frog_p_1_a <- ggplot(data = frog_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM4 + Plt+  Xlab1 +  Ylab1 +  FW 
frog_p_1_a 

 
 #ggsave("frogs_plot1_avg.jpg")



##frog plot 2


frog_p_2_a <- ggplot(data = frog_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
frog_p_2_a

 
 #ggsave("frogs_plot2_avg.jpg", width = W2, height = H2)

```


## katydids
katydid plot 1
```{r}
katydid <- subset( g_u, g_u$Playback == "A. spatulata" | g_u$Playback == "C. wheeleri" | g_u$Playback == "D. gigliotosi"| g_u$Playback == "T. subfalcata" | g_u$Playback =="V. zederstedi")

katydid_p_1 <- ggplot(data = katydid, aes(x = Playback, y = Response, colour = Species_full))    + G + C  + TM3 + Plt+  Xlab1 +  Ylab1 +  FW 
katydid_p_1

 
 #ggsave("katydids_plot1_axis.jpg")



```
katydid plot 2
```{r}

katydid_p_2 <- ggplot(data = katydid, aes(x = Species_full, y = Response, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 +FW2
katydid_p_2 

 
 #ggsave("katydids_plot2.jpg", width = W2, height = H2)

```

## katydids averages
katydid plot 1
```{r}
katydid_avg <- subset( Resp_avg, Resp_avg$Playback == "A. spatulata" | Resp_avg$Playback == "C. wheeleri" | Resp_avg$Playback == "D. gigliotosi"| Resp_avg$Playback == "T. subfalcata" | Resp_avg$Playback =="V. zederstedi")

katydid_p_1_a <- ggplot(data = katydid_avg, aes(x = Playback, y = Resp_average, colour = Species_full))    + G + C  + TM3 + Plt+  Xlab1 +  Ylab1 +  FW 
katydid_p_1_a 

 
 #ggsave("katydids_plot1_avg_axis.jpg")



##katydid plot 2


katydid_p_2_a <- ggplot(data = katydid_avg, aes(x = Species_full, y = Resp_average, colour = Species_full))   + GG2  + C2 + TM3 + Plt2 + Xlab2 +Ylab2 + FW2
katydid_p_2_a

 
 #ggsave("katydids_plot2_avg.jpg", width = W2, height = H2)

```


##########################
##########################

```{r}


rankModels = function(mod,names=NULL,phi=NULL,pretend=NULL) {
  
  # Overdispersion
  # calculate Pearson Chi squared
  if (is.null(phi)==FALSE) {
    if (is.numeric(phi)){phi=phi}
    else {
      X2 <- sum(residuals(phi, type = "pearson")^2)
      
      
      # divide by the residual degrees of freedom
      phi <- X2/phi$df.residual
    }}
  # can also calculate with residual deviance
  print(phi)
  if(is.null(pretend)){pretend=TRUE}
  if (is.null(names)==FALSE){names = names[2:length(names)]}  
  if (is.null(names)==TRUE){names = paste("m",1:length(mod),sep="")}  
  Model   = 1:length(mod)
  LogLik     = vector(length = length(mod))
  ll      = vector(length = length(mod))
  n       = vector(length = length(mod))
  p       = vector(length = length(mod))
  AICc    = vector(length = length(mod))
  AIC     = vector(length = length(mod))
  RootMSE = vector(length = length(mod))
  
  
  
  # Make sure all models in list are either glm or lme4 objects. You can't compare mixed and fixed effects models.  
  allright=FALSE
  cl = character(length=length(mod))
  for (ii in 1:length(mod)){
    cl[ii] = class(mod[[ii]])[1] # identify the class of each model object in the list 
  }
  if (all(cl=="nlme") | all(cl=="nls") | all(cl=="gam") | all(cl=="betareg")| all(cl=="mer"|cl=="glm") | all(cl=="clmm" | cl=='sclm')) {allright=TRUE}

  
  if (allright==TRUE){
    # loop over the models in the list to extract relevant info.
    for (m in 1:length(mod)) {
      LogLik[m]      = logLik(mod[[m]])
      ll[m]      = as.numeric(LogLik[m])
      p[m]      = attr(logLik(mod[[m]]),"df")
      
      if (cl[m]=="mer"){
        r         = mod[[m]]@y - fitted(mod[[m]])} # get y from lme4 object
      
      if (cl[m]=="clmm"|cl[m]=="sclm"){
        # can't calculate residual variance for clmm models, so set to 0
        r         = rep(0,dim(mod[[m]]$model[1])[1])} 
      
      if  (cl[m] %in% c("glm","gam","betareg")) {
        r       = mod[[m]]$y - fitted(mod[[m]])}
      
      if (cl[m]=="nlme") {
        r       = mod[[m]]$residuals[,1]}  # get r from nlme object
      
      if (cl[m]=="nls") {
        r       = as.numeric(resid(mod[[m]]))}  # get r from nls object
      
      
      # calculate RMSE for all but clmm models
      RootMSE[m]= sqrt(sum(r^2))
      if (cl[m]=="clmm"|cl[m]=="sclm"){RootMSE[m]=NA}
      n[m] = length(r)
      if (is.null(phi)){
        AICc[m]   = as.numeric(-2 * ll[m] + 2*p[m] + 2*p[m]*(p[m] + 1)/(n[m] - p[m] - 1))
        AIC[m]    = as.numeric(-2 * ll[m] + 2*p[m])
      }
      else{
        if (is.null(phi)==FALSE){
          AICc[m]   = as.numeric(-2 * ll[m]/phi + 2*p[m] + 2*p[m]*(p[m] + 1)/(n[m] - p[m] - 1))
          AIC[m]    = as.numeric(-2 * ll[m]/phi + 2*p[m])
        }
      }
    }
    
    ###############################################################################
    # try to identify pretending models
    # calcualte all pairwise delta AIC values so we can identify pairs of models with delta AIC approximately     twice the difference in their number of parameters.
    
    daic = matrix(0,length(Model),length(Model))
    dll  = matrix(0,length(Model),length(Model))
    llDir  = matrix(0,length(Model),length(Model))
    dp   = matrix(0,length(Model),length(Model))
    for (ii in 1:length(Model)){
      for (iii in 1:length(Model)){
        dll[ii,iii] = ll[ii]-ll[iii]
        llDir[ii,iii] = ll[ii]>ll[iii]
        daic[ii,iii] = AIC[ii]-AIC[iii]
        dp[ii,iii]   = p[ii]-p[iii]
      }
    }
    
    # identify model pairs with close log likelihood values
    sameLL = dll>0 & dll<=0.5
    
    # identify model pairs whose difference in the number of parameters is roughly divisible by 2, which is the per-parameter penalty used in calculating AIC.  
    paramDif = (1 - daic/(dp*2))<0.2 & (1 - daic/(dp*2))>0
    
    # identify model pairs that meet both conditions. The column index should be the 'real' model, and the row index is the column;
    impostors = which(sameLL & paramDif,arr.ind=TRUE)
    
    
    delAIC = AICc-min(AICc)                      # Delta AICc
    W = exp(-0.5*delAIC)/sum(exp(-0.5*delAIC))   # Akaike Weight
    Wp = rep(0,length(Model))
    Wp[-impostors[,1]] = exp(-0.5*delAIC[-impostors[,1]])/sum(exp(-0.5*delAIC[-impostors[,1]]))   # Akaike Weight
    
    Pretending = character(length(Model))
    for (ii in 1:length(Model)){
      if(any(impostors[,2]==ii)){
        if(is.null(names)){getImpostors = as.character((c(impostors[impostors[,2]==ii,1])))}
        if(is.null(names)==FALSE){getImpostors = names[(c(impostors[impostors[,2]==ii,1]))]}
        Pretending[ii] = paste(getImpostors,collapse=", ") }}
    
    idx = sort(delAIC,index.return=TRUE)         # create index to sort by deltaAICc
    
    # Sort variables by index to output to table
    if (is.null(names)==TRUE){Model = Model[idx$ix]}  # model id number
    if (is.null(names)==FALSE){Model = names[idx$ix]} # model name if available
    LogLik      = formatC(LogLik[idx$ix],2,format="f")   # log likelihood
    p        = p[idx$ix]                           # number of parameters
    AICc     = formatC(AICc[idx$ix],2,format="f")  # AICc or QAICc
    RootMSE  = RootMSE[idx$ix]                     # RMSE - a measure of variance explained
    delAICc  = formatC(delAIC[idx$ix],2,format="f")# delta AICc or QAICc
    W        = formatC(W[idx$ix],3,format="f")     # Akaike weights
    Wp       = formatC(Wp[idx$ix],3,format="f")     # Akaike weights without pretending models
    Pretending= Pretending[idx$ix]
    
    # make table withouth phi
    if (is.null(phi)){
      if(pretend){modelTable = data.frame(Model,LogLik,n,p,AICc,delAICc,W,RootMSE,Wp,Pretending)}
      else{if (pretend==FALSE){modelTable = data.frame(Model,LogLik,n,p,AICc,delAICc,W,RootMSE)}}}
    
    # make table with phi (if dispersion parameter is supplied)
    if (is.null(phi)==FALSE){
      QAICc = AICc
      delQAICc = delAICc;
      if (pretend){modelTable = data.frame(Model,LogLik,n,p,QAICc,delQAICc,W,RootMSE,Wp,Pretending)}
      else{if (pretend==FALSE){modelTable = data.frame(Model,LogLik,n,p,QAICc,delQAICc,W,RootMSE)}}
    }
    modelTable # return table
  } else {
    warning("All models must be either glm or lme4 objects.",call=TRUE)
  }
}
```



Stats?

DO different bats have different preferences?
```{r}
################ Can put this stat on chart: Different species respond to sounds differently
#no AJS
g_u_2<- subset(g_u, g_u$species != Arti_jama)

#DO different bats have different responses to sounds?
#Response score ~Playback
#clmm

G_U_clmm_pl<- clmm(as.factor(Response) ~ Species + (1| Number) + (1| ID), data= g_u)
summary(G_U_clmm_pl)

sp_em <-emmeans(G_U_clmm_pl, "Species")
sp_em
sp_em_cld<- cld(sp_em, letters=LETTERS)
sp_em_cld
plot(sp_em)

#ggsave("emmeans_all_pl.jpg")

```


RUNNING TESTS TO SEE WHETHER DIFFERENT BATS RESPOND TO SOUNDS DIFFERENTLY
```{r}
#Does playback predict response? Yes
G_U_clmm_pl<- clmm(as.factor(Response) ~ Playback + (1| ID), data= g_u)
summary(G_U_clmm_pl) 

# Does category predict response? YES
G_U_clmm_CT<- clmm(as.factor(Response) ~ Call_type + (1| ID), data= g_u)
summary(G_U_clmm_CT) 
em_CT <-emmeans(G_U_clmm_CT, "Call_type")
em_CT
plot(em_CT)
# ggsave("over_bat_response_call_type.jpg")
G_U_clmm<- clmm(as.factor(Response) ~ Species*Playback + (1| Number), data= g_u)
summary(G_U_clmm)


g1_01<- clmm(as.factor(Response) ~ Species * Playback + (1|ID), data= g_u, Hess=TRUE, nAGQ=10) #full model
g1_02<- clmm(as.factor(Response) ~ Species + Playback + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)
g1_03<- clmm(as.factor(Response) ~ Species + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)
g1_04<- clmm(as.factor(Response) ~ Playback + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)
g1_05<- clmm(as.factor(Response) ~ 1 + (1|ID), data= g_u, Hess=TRUE, nAGQ=10)

rankModels(list(g1_01, g1_02, g1_03, g1_04, g1_05))
rankedmodels_g1<-rankModels(list(g1_01, g1_02, g1_03, g1_04, g1_05))
rankedmodels_g1
## So this analysis thinks that species predicts responses, and playback predicts responses, but different species don't respond differently to different playbacks (including all the species with more than 1 response. But the first model was just really hard to fit. May be that mostly bats responded to the sounds just as hthings to listen to, and since most of the bats didn't respond to sounds, then that was the dominant effect)

#1 pull out species with at least 1 land, and test them, to pull out species that we know are paying attention for food purposes. 

#could also do an analysis with the bats that are most likely to just be listening: AJS, discolor. try to parse what just listening looks like vs what hunting looks like. 

# also pull out a species and look at preferences

```

TEST ACOUSTIC PREFERENCES: MULTICOLLINEARITY
```{r}
# Make models to test for Multicollinearity, choose variables that don't super covary
g_u$pulses_call <- as.numeric(g_u$pulses_call)
g_u$duty_cycle<- as.numeric(g_u$duty_cycle)
g_u$sum_pulse_duration_callgroup <- as.numeric(g_u$sum_pulse_duration_callgroup)

## pretty nuch every acoustic variable must be logged
hist(g_u$amplitude)
hist(log(g_u$amplitude))

#  removed variables+ log(pulses_call)
model <- glm(Response ~ log(sum_pulse_duration_callgroup) + log(peak_freq) + log(bandw)   + log(duty_cycle) + log(file_time_with_sound) + amplitude , data= g_u)
summary(model)
alias(model)
vif(model) 

# with call types logged, these are not multicollinear > 5

```





```{r}
as.numeric(g_u$duty_cycle)
colnames(g_u)
G_U_acoustic<- clmm(as.factor(Response) ~ sum_pulse_duration_callgroup + peak_freq + bandw + pulses_call  + duty_cycle + file_time_with_sound + amplitude + (1| Number), data= g_u)
summary(G_U_acoustic)

```

Do different bats have different responses to white noise? 

```{r}
White #

G_U_clmm_white<- clmm(as.factor(Response) ~ Species + (1| Number), data= g_u[  g_u$Playback==c("White noise"), ])

summary(G_U_clmm_pl)
```


Do different bats have different responses to katydids? 

BY BAT SPECIES
```{r}
katydid #data

G_U_clmm_k_pl<- clmm(as.factor(Response) ~ Species + (1| Number), data= katydid)
summary(G_U_clmm_k_pl)

K_pl<-emmeans(G_U_clmm_k_pl, "Species")
K_pl
K_pl_cld<- cld(K_pl, letters=LETTERS)
K_pl_cld
plot(K_pl_cld) #overall responses to katydids
#ggsave("emmeans_katydid_pl.jpg")

## BY KATYDID
katydid1 <- katydid
katydid1$Playback <- as.character(katydid1$Playback)

G_U_clmm_k_pl<- clmm(as.factor(Response) ~ as.character(Playback) + (1| Number), data= katydid1)
summary(G_U_clmm_k_pl)

K_pl<-emmeans(G_U_clmm_k_pl, "Playback")
K_pl
K_pl_cld<- cld(K_pl, letters=LETTERS)
K_pl_cld
plot(K_pl_cld) #overall responses to katydids
#ggsave("emmeans_K_pl.jpg")

```





#####SOUND#######







